---
title: "compile_2020"
output: html_document
---


```{r Load in libs, set project dirs}
library(tidyverse)

root.dir <- rprojroot::find_root("chem_hist_cleaning.Rproj")
target.dir <- file.path(root.dir, "data", "2020")
qaqc_dir <- file.path(target.dir, "qaqc_output")
datamod.dir <- "C:/Users/gmlemley/New York State Office of Information Technology Services/SMAS - Streams Data Modernization/Cleaned Files/Final_Chemistry_ITS/"

```

Import sample and result files exported from Chem_raw_processing.Rproj
```{r Import data}
sample.all <- read.csv(file.path(target.dir, "2020_chem_preqaqc_SAMPLE-ALL_2021-04-13.csv"), stringsAsFactors = FALSE)
result.all <- read.csv(file.path(target.dir, "2020_chem_preqaqc_RESULT-ALL_2021-04-13.csv"), stringsAsFactors = FALSE) %>% 
  rename(sample_delivery_group = lab_sdg)

```

Test join by sys_sample_code and SDG
```{r Initial join test}
test_join_sample.result <- full_join(sample.all, result.all, by = c("sys_sample_code", "sample_delivery_group"))

# CHECKS OUT OKAY. Same number of records created in joined table as in RESULT table.

rm(test_join_sample.result)
```

Import and bind flags from QAQC output files
```{r Import QAQC flags}
# Import all qaqc output files in subdir and bind together as a dataframe
setwd(qaqc_dir)
qaqc.output.bound <- list.files(path = qaqc_dir, pattern = "*.csv") %>% 
  map_df(~read_csv(.,  col_types = cols(fraction = col_character()))) %>% 
  # mutate(project_name = str_replace(project_name, "RIBS_", "")) %>% 
  # mutate(project_name = str_replace(project_name, " - ", "_")) %>% 
  # mutate(project_name = str_replace(project_name, "_-_", "_")) %>% 
  # mutate(project_name = str_replace_all(project_name, " ", "_")) %>% 
  mutate(chemical_name = tolower(chemical_name))

# Select only fields needed to join to results table and mark all as validated 
qaqc.output.bound <- qaqc.output.bound %>%
  select(project_name, sys_sample_code, sample_delivery_group, chemical_name, fraction, validator_qualifiers, interpreted_qualifiers, qaqc_date) %>%
  mutate(validated_yn = "Y") %>%
  rename(VALIDATOR_QUAL_EXPLN = interpreted_qualifiers)

```

Join flags and related fields to results table
```{r Join QAQC flags}
result.all <- result.all %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  select(-validated_yn, -validator_qualifiers)

# Test various joins and compare to identify possible issues
result.all.flags.left <- left_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.all.flags.full <- full_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# Resulting left and full joins are identical (no recs left behind)

result.all.flags.inner <- inner_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# matches number of QAQC records in chunk above (all have match)

# Do antijoin to make sure non-joined records are all lab and QC samples.
result.all.flags.anti <- anti_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.sample.anti <- right_join(sample.all, result.all.flags.anti, by = c("sys_sample_code", "sample_delivery_group"))

# filter to non-lab and QC samples to verify what's missing was intentional

result.sample.anti.sub <- result.sample.anti %>% 
  filter(sample_type_code %in% "N",
         DEC_sample_type %in% "N") 

# > sort(unique(result.sample.anti.sub$SITE_ID))
# [1] "03-EMIL-5.1"  "13-LMOHE-0.0" "13-LPEAC-0.0" "13-LPNAM-0.0"

# Found: Non-flagged sites above: PCBs at Eighteenmile, and 3 sediment samples for Lakes biomonitoring.

#  Look for duplicate records (possible issues with join)
dups <- result.all.flags.full %>% 
  group_by(sys_sample_code, sample_delivery_group, chemical_name, fraction) %>% 
  mutate(dups = n()) %>% 
  filter(dups > 1)
 # Found: Only dups present are with PCBs and they are present in the raw EDDs.

# Clean up dataframes and rename
result.all <- result.all.flags.full
rm(qaqc.output.bound, result.all.flags.left, result.all.flags.full, result.all.flags.inner, result.all.flags.anti, result.sample.anti, result.sample.anti.sub, dups)

```

Flag any field results not run through QAQC
```{r Populated flags fir non-QAQC'd data}
# Join sample type field from SAMPLE table to gather required info for filtering
sample.all.type <- sample.all %>% 
  select(SITE_ID, sys_sample_code, sample_source, sample_delivery_group, DEC_sample_type, sample_type_code)
result.all.type <- left_join(result.all, sample.all.type, by = c("sys_sample_code", "sample_delivery_group")) %>% 
  # select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, validator_qualifiers, VALIDATOR_QUAL_EXPLN, everything())
  select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, everything())

# Check what types of samples got flags
result.all.type.check <- result.all.type %>% 
  select(validator_qualifiers, DEC_sample_type) %>% 
  distinct()

# Filter out normal samples that didn't get flags to verify that only the ones intentionally not flagged are there.
result.all.notflagged.n <- result.all.type %>% 
  filter(is.na(validator_qualifiers),
         DEC_sample_type %in% "N",
         sample_source %in% "Field")

# > sort(unique(result.all.notflagged.n$SITE_ID))
# [1] "03-EMIL-5.1"  "13-LMOHE-0.0" "13-LPEAC-0.0" "13-LPNAM-0.0"
# Found: As expected. All good.

# Mark validated_yn as "N" for all those above then add NF flags and explanations to all those above 
# except EMIL and MOHK+UHUD-2.7 sites. [E; Error flag; commented out but retainted for future use]

result.all.flagged2 <- result.all.type %>% 
  mutate(validated_yn = ifelse(
    is.na(validator_qualifiers) &
      DEC_sample_type %in% "N" &
      sample_source %in% "Field",
    "N", validated_yn)) 
  # mutate(validator_qualifiers = ifelse(
  #   is.na(validator_qualifiers) &
  #     DEC_sample_type %in% "N" &
  #     sample_source %in% "Field" &
  #     !grepl("*EMIL", SITE_ID) &
  #     !grepl("*UHUD", SITE_ID) &    # Added 2020-10-05
  #     !grepl("*MOHK", SITE_ID), 
  #   "E", validator_qualifiers)) %>% 
  # mutate(VALIDATOR_QUAL_EXPLN = ifelse(validator_qualifiers %in% "E", 
  #   "Not flagged due to QAQC error or insufficient QAQC sampling", VALIDATOR_QUAL_EXPLN)) 

# Verify that only remaining field "N" samples without flags are those params we don't flag (PCBs and 5 DBP surrogate params)
result.all.flagged2.naflags <- result.all.flagged2 %>% 
  filter(is.na(validator_qualifiers),
         sample_source %in% "Field",
         DEC_sample_type %in% "N")
# Above checks out :)

# Clean up new result table and remove joined fields
result.all.flagged2 <- result.all.flagged2 %>% 
  select(-SITE_ID, -sample_source, -DEC_sample_type, -sample_type_code) 

rm(sample.all.type, result.all.type, result.all.type.check, result.all.notflagged.n, result.all.flagged2.naflags)


```

Fix EB samples misidentified as FB in ALS data
```{r Look for misidentified QC samples}

# Find sys_sample_codes that have FB but are not mercury results
result.badFBs <- result.all.flagged2 %>% 
  filter(grepl("*FB", sys_sample_code),
         !grepl("mercury", chemical_name)
  )
# Found: None! Commented out remaining chunk and moved on.

# badFB.SSCs <- result.badFBs %>% 
#   select(sys_sample_code) %>% 
#   distinct() %>% 
#   # Adde EB field to list of bad SSCs to join 
#   mutate(DEC_sample_type.corr = "EB")
# 
# # Pull list of matching samples in SAMPLE table and check if all FBs
# sample.badFB.match <- sample.all %>% 
#   filter(sys_sample_code %in% badFB.SSCs$sys_sample_code)
# 
# # Change DEC sample type codes for the list above from FB to EB
# sample.all <- sample.all %>% 
#   left_join(badFB.SSCs, by = "sys_sample_code") %>% 
#   mutate(DEC_sample_type = ifelse(DEC_sample_type.corr %in% "EB", "EB", DEC_sample_type)) %>% 
#   select(-DEC_sample_type.corr)

rm(result.badFBs, badFB.SSCs, sample.badFB.match)

```

Remove special character from lab_qualifiers and interpreted_qualifiers fields (subcontracted data uses commas and sometimes brackets)
```{r Clnea up lab flags}
# Make table of unique flags and test methods of removing special characters
labflags <- result.all.flagged2 %>% 
  select(lab_qualifiers, interpreted_qualifiers, sample_delivery_group) %>% 
  distinct(lab_qualifiers, interpreted_qualifiers, .keep_all = TRUE)
  
#Found: "[B]" flag in subcontracted PCB data. Verified with lab there is no significance to the brackets.

labflags.edit <- labflags %>%
  mutate(lab_qualifiers2 = str_replace_all(lab_qualifiers, "[^[:alnum:]]", "")) %>% 
  mutate(interpreted_qualifiers2 = str_replace_all(interpreted_qualifiers, "[^[:alnum:]]", ""))

labflags.new <- labflags.edit %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()

result.all.flagged2 <- result.all.flagged2 %>% 
  mutate(lab_qualifiers = str_replace_all(lab_qualifiers, "[^[:alnum:]]", "")) %>% 
  mutate(interpreted_qualifiers = str_replace_all(interpreted_qualifiers, "[^[:alnum:]]", ""))
  
labflags.new2 <- result.all.flagged2 %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()

rm(labflags, labflags.edit, labflags.new, labflags.new2)

```

Review for T/D reporting issues in Routine
Make sure c("aluminum", "cadmium", "copper", "lead", "nickel", "zinc") are all reported as only dissolved fractions. If not, check reports to verify they were analyzed as such.

```{r ID and fix fraction reporting issues}

#Load in routine sites list
routine.sites <- readxl::read_excel("C:\\Users\\gmlemley\\New York State Office of Information Technology Services\\SMAS - Routine Network\\Sites and staff info\\RIBS_ROUTINE_SITES_REGION_INFO_2020-09-14.xlsx") %>% 
  select("SBU ID")

# Join result and sample, filter to Routine sites and relevent fields for review 
samp.res.routine <- left_join(sample.all, result.all.flagged2, by = c("sys_sample_code", "sample_delivery_group")) %>% 
  filter(SITE_ID %in% routine.sites$`SBU ID`,
         sample_source %in% "Field",
         DEC_sample_type %in% c("N", "N_DUPPARENT")) %>% 
  mutate(year = substr(sample_date, 7, 10),
         month = substr(sample_date, 0, 2)) %>% 
  select(SITE_ID, fraction, month, year, sys_sample_code, sample_delivery_group, sample_date, chemical_name) 

# samp.res.routine.bad <- samp.res.routine %>% 
#   filter(sample_delivery_group %in% c("R1803378", "R1807696", "R1905509", "R1910407", "R1910662"),
#          chemical_name %in% c("aluminum", "cadmium", "copper", "lead", "nickel", "zinc")) 

# Look for T fraction in below then ID which params are affected in above 
samp.res.routine.dissmetals <- samp.res.routine %>% 
  filter(chemical_name %in% c("aluminum", "cadmium", "copper", "lead", "nickel", "zinc")) %>% 
  select(-chemical_name) %>% 
  distinct()

# Found: August Bronx river Aluminum result was mislabeled T. Verified D in report. Fixed in below.

result.all.flagged2.test <- result.all.flagged2 %>% 
  mutate(fraction = ifelse(grepl("17-BRNX-5.6-08132020-W", sys_sample_code)  & chemical_name %in% "aluminum", "D", fraction))

rm(result.all.flagged2.test, samp.res.routine, samp.res.routine.dissmetals, routine.sites)

result.all.flagged2 <- result.all.flagged2 %>% 
  mutate(fraction = ifelse(grepl("17-BRNX-5.6-08132020-W", sys_sample_code)  & chemical_name %in% "aluminum", "D", fraction))

```


Join pcodes field using "pcode join table" (based on chemical_name, fraction, and unit)
```{r Join pcodes}

# Import pcodes 
# pcode_path <- file.path("C:/Users/gmlemley/New York State Office of Information Technology Services/SMAS - Streams Data Modernization/to_be_cleaned/chem_parameters")
# pcode.join <- readxl::read_excel(file.path(pcode_path, "pcode_join_table_CLEAN_2020-06-25.xlsx")) %>% 
pcode.join <- read_csv(file.path(root.dir, "parameters", "dec_pcode_join_2021-04-14.csv")) %>%
  select(RESULT_TYPE, everything()) %>% 
  # select(-"Has duplicate", -"Notes") %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  mutate(result_unit = tolower(result_unit)) %>% 
  mutate(DEC_pcode_FINAL = formatC(DEC_pcode_FINAL, width = 3, format = "d", flag = "0")) %>% 
  # Remove instances of duplicate rows that represented differing unit capitalization (will just do this in the data) 
  distinct()

# Export cleaned pcode table for sending to LMAS
# write.csv(pcode.join, file.path(root.dir, "parameters", "dec_pcode_join_2020-08-24.csv"), row.names = FALSE)

# Filter to lab only for joining to chem data
pcode.join.lab <- pcode.join %>% 
  filter(RESULT_TYPE %in% "lab") %>%
  select(-RESULT_TYPE)

# Join to chem results table
result.all.pcodes <- left_join(result.all.flagged2, pcode.join.lab, by = c("chemical_name", "fraction", "result_unit")) %>% 
  select(DEC_pcode_FINAL, chemical_name, everything())

# Return records that didn't get pcodes assigned
result.all.pcodes.na <- result.all.pcodes %>% 
  filter(is.na(DEC_pcode_FINAL))
sort(unique(result.all.pcodes.na$chemical_name))

## Populate missing pcodes
# Commented out after updating pcode join table to included all PCBs.

# # Use list to ID PCB params other than pcode 167 (total pcbs), which should already be joined from the pcode table
# pcb.names <- c("*pcb", "*iupac", "*chlorobiphenyl")
# result.all.pcodes <- result.all.pcodes %>% 
#     mutate(DEC_pcode_FINAL = ifelse(is.na(DEC_pcode_FINAL) & grepl(paste(pcb.names,collapse="|"), chemical_name) & result_unit %in% "pg/l", 168, DEC_pcode_FINAL)) %>% 
#       mutate(DEC_pcode_FINAL = ifelse(is.na(DEC_pcode_FINAL) & grepl(paste(pcb.names,collapse="|"), chemical_name) & result_unit %in% "percent", 169, DEC_pcode_FINAL))
# 
# # Again, return records that didn't get pcodes assigned
# result.all.pcodes.na <- result.all.pcodes %>% 
#   filter(is.na(DEC_pcode_FINAL))
# sort(unique(result.all.pcodes.na$chemical_name))

# summarize join for review  
result.all.pcodes.check <- result.all.pcodes %>%
  select(DEC_pcode_FINAL, chemical_name, fraction, result_unit) %>%
  distinct()

result.all <- result.all.pcodes

rm(result.all.pcodes, pcode.join, pcode.join.lab, result.all.flagged2, result.all.pcodes.na, result.all.pcodes.check)


```

Look for bad dates from ALS
```{r ID bad dates}
# Identify bad years in sample_date and analysis_date fields as found in previous deliveries

## SAMPLE

# Look for bad years
sample.all.datecheck <- sample.all %>% 
  filter(!grepl("*2020", sample_date))

# Found: None!

# # Test mutation
# sample.all.datecheck <- sample.all.datecheck %>% 
#   mutate(sample_date = str_replace(sample_date, "1999", "2019")) %>% 
#   mutate(sample_date = str_replace(sample_date, "2016", "2019"))
# 
# # Perform mutation
# sample.all.corr <- sample.all %>% 
#   mutate(sample_date = str_replace(sample_date, "1999", "2019")) %>% 
#   mutate(sample_date = str_replace(sample_date, "2016", "2019"))
# 
# sample.all <- sample.all.corr

rm(sample.all.datecheck, sample.all.corr)


## RESULT

# Find bad years
result.all.form.datecheck <- result.all %>% 
  filter(!grepl("*2020", analysis_date))

# Found: None!


# # Test mutation
# result.all.form.datecheck <- result.all.form.datecheck %>% 
#   mutate(analysis_date = str_replace(analysis_date, "1999", "2019")) %>% 
#   mutate(analysis_date = str_replace(analysis_date, "2016", "2019"))
# 
# # Perform mutation
# result.all.corr <- result.all %>% 
#   mutate(analysis_date = str_replace(analysis_date, "1999", "2019")) %>% 
#   mutate(analysis_date = str_replace(analysis_date, "2016", "2019"))
# 
# result.all <- result.all.corr

rm(result.all.form.datecheck, result.all.corr)

```

Reformat field names
```{r Reformat field names}

## For 2018-2019: Join project name to sample table for exporting for Charlie (to verify project table)
# result.projnames <- result.all %>% 
#   select(sample_delivery_group, project_name) %>% 
#   filter(!is.na(project_name)) %>% 
#   unique()
# sample.all.projnames <- left_join(sample.all, result.projnames, by = "sample_delivery_group") %>%
#   select(project_name, sample_date, everything()) %>%
#   filter(sample_source %in% "Field")
# write.table(sample.all.projnames, file = file.path(root.dir, "data", "2018-2019_ITS_2020-08-25", "chem_sample_2018-2019_fieldonly_projnames.csv"),sep=",", row.names = FALSE)


sample.all.form <- sample.all %>%
  rename_all(toupper) %>%
  rename(
    EVENT_SMAS_HISTORY_ID = SITE_ID,
    DEC_SAMPLE_TYPE_CDE = DEC_SAMPLE_TYPE,
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    SAMPLE_MATRIX_CDE = SAMPLE_MATRIX_CODE,
    LAB_SAMPLE_TYPE_CDE = SAMPLE_TYPE_CODE,
    PARENT_SAMPLE_CDE = PARENT_SAMPLE_CODE,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP,
    SYS_LOC_CDE = SYS_LOC_CODE,
    SAMPLE_DATETIME = SAMPLE_DATE,
    SITE_ID_CORR_YN = SITE_ID_CORR_IND
  ) %>%
  mutate(SAMPLE_DATETIME.posixct = as.POSIXct(SAMPLE_DATETIME, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(EVENT_SMAS_SAMPLE_DATE = strftime(SAMPLE_DATETIME.posixct, "%m/%d/%Y")) %>%
  rename_all(function(x)
    paste0("CHS_", x))
# mutate(EVENT_SMAS_ID = paste0(CHS_SITE_ID,"_",EVENT_ID_DATE))

result.all.form <- result.all %>%
  rename_all(toupper) %>%
  mutate(QLFR_SRC = "AE") %>% 
  rename(
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME,
    LAB_MATRIX_CDE = LAB_MATRIX_CODE,
    LAB_NAME_CDE = LAB_NAME_CODE,
    SUBSAMPLE_AMT = SUBSAMPLE_AMOUNT,
    SUBSAMPLE_AMT_UNIT = SUBSAMPLE_AMOUNT_UNIT,
    RESULT_TYPE_CDE = RESULT_TYPE_CODE,
    # REPORTABLE_RESULT_IND = REPORTABLE_RESULT,
    LAB_QUAL = LAB_QUALIFIERS,
    VALIDATOR_QUAL = VALIDATOR_QUALIFIERS,
    INTERPRETED_QUAL = INTERPRETED_QUALIFIERS,
    # VALIDATED_IND = VALIDATED_YN,
    METHOD_DETECT_LIMIT = METHOD_DETECTION_LIMIT,
    REPORTING_DETECT_LIMIT = REPORTING_DETECTION_LIMIT,
    QC_ORIG_CONC = QC_ORIGINAL_CONC,
    QC_DUP_ORIG_CONC = QC_DUP_ORIGINAL_CONC,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP,
    VALIDATION_DATE = QAQC_DATE
  ) %>%
  # mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  # mutate(PREP_DATE = as.POSIXct(PREP_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(VALIDATION_DATE = as.Date(VALIDATION_DATE, format = "%m/%d/%Y"),
         VALIDATION_DATE = format((VALIDATION_DATE), "%m/%d/%Y")) %>% 
  mutate(FRACTION = case_when(
    FRACTION == "T" ~ "TOTAL",
    FRACTION == "D" ~ "DISSOLVED",
    TRUE ~ FRACTION)) %>% 
  rename_all(function(x)
    paste0("CHR_", x)) %>% 
  rename(CHR_PCODE = CHR_DEC_PCODE_FINAL)
    # fixed above from CHEM_PCODE on 9/11/20.

```

Select final headers as per ITS data model
```{r Select final columns}

# SAMPLE table
sample.all.FINAL <- sample.all.form %>% 
    select(CHS_EVENT_SMAS_HISTORY_ID, CHS_EVENT_SMAS_SAMPLE_DATE, CHS_SITE_ID_CORR_YN, CHS_DATA_PROVIDER, CHS_SYS_SAMPLE_CDE, 
           CHS_SAMPLE_NAME, CHS_SAMPLE_MATRIX_CDE, CHS_DEC_SAMPLE_TYPE_CDE, CHS_LAB_SAMPLE_TYPE_CDE, CHS_SAMPLE_SOURCE, 
           CHS_PARENT_SAMPLE_CDE, CHS_SAMPLE_DEL_GRP, CHS_SAMPLE_DATETIME, CHS_SAMPLE_RECEIPT_DATE, CHS_SYS_LOC_CDE,
           CHS_CHAIN_OF_CUSTODY, CHS_SAMPLER, CHS_SAMPLING_COMPANY_CODE, CHS_COMMENT)

# RESULT table
result.all.FINAL <- result.all.form %>% 
  select(CHR_PCODE, CHR_SYS_SAMPLE_CDE, CHR_SAMPLE_DEL_GRP, CHR_LAB_ANAL_METHOD_NAME, CHR_ANALYSIS_DATE, CHR_TEST_TYPE, CHR_LAB_MATRIX_CDE, 
         CHR_DILUTION_FACTOR, CHR_PREP_METHOD, CHR_PREP_DATE, CHR_LAB_NAME_CDE, CHR_QC_LEVEL, CHR_LAB_SAMPLE_ID, CHR_SUBSAMPLE_AMT, 
         CHR_SUBSAMPLE_AMT_UNIT, CHR_FINAL_VOLUME, CHR_FINAL_VOLUME_UNIT, CHR_CAS_RN, CHR_RESULT_VALUE, 
         CHR_RESULT_TYPE_CDE, CHR_REPORTABLE_RESULT, CHR_DETECT_FLAG, CHR_QLFR_SRC, CHR_LAB_QUAL, CHR_VALIDATED_YN, CHR_VALIDATION_DATE, CHR_VALIDATOR_QUAL, 
         CHR_VALIDATOR_QUAL_EXPLN, CHR_METHOD_DETECT_LIMIT, 
         CHR_REPORTING_DETECT_LIMIT, CHR_QUANTITATION_LIMIT, CHR_DETECTION_LIMIT_UNIT, CHR_RESULT_COMMENT, CHR_QC_ORIG_CONC, 
         CHR_QC_SPIKE_ADDED, CHR_QC_SPIKE_MEASURED, CHR_QC_SPIKE_RECOVERY, CHR_QC_DUP_ORIG_CONC, CHR_QC_DUP_SPIKE_ADDED, CHR_QC_DUP_SPIKE_MEASURED, 
         CHR_QC_DUP_SPIKE_RECOVERY, CHR_QC_RPD, CHR_QC_SPIKE_LCL, CHR_QC_SPIKE_UCL, CHR_QC_RPD_CL, CHR_QC_SPIKE_STATUS, CHR_QC_DUP_SPIKE_STATUS, 
         CHR_QC_RPD_STATUS)

```

Convert NAs to text for not_null fields (for coded tables)
```{r Convert NAs for non_nulls}
result.all.FINAL <- result.all.FINAL %>% 
  mutate(CHR_LAB_QUAL = ifelse(is.na(CHR_LAB_QUAL), 0, CHR_LAB_QUAL),
         CHR_LAB_QUAL = ifelse(CHR_LAB_QUAL %in% "", 0, CHR_LAB_QUAL),
         CHR_VALIDATOR_QUAL = ifelse(is.na(CHR_VALIDATOR_QUAL), 0, CHR_VALIDATOR_QUAL))
```


Generate list of unique values for review
```{r View unique values, eval = FALSE}

sample.unique <- lapply(sample.all.FINAL, unique)
result.unique <- lapply(result.all.FINAL, unique)

```



```{r Other final modifications}

# Change DEC sample type DUPs to SEQs (switched starting in 2020 to differentiate from old dup type)
# Format dates as dates to verify by sorting, then to the proper ITS format.
sample.all.FINAL <- sample.all.FINAL %>% 
  mutate(CHS_DEC_SAMPLE_TYPE_CDE = ifelse(CHS_DEC_SAMPLE_TYPE_CDE %in% "DUP", "SEQ", CHS_DEC_SAMPLE_TYPE_CDE),
         CHS_DEC_SAMPLE_TYPE_CDE = ifelse(CHS_DEC_SAMPLE_TYPE_CDE %in% "N_DUPPARENT", "N_SEQPARENT", CHS_DEC_SAMPLE_TYPE_CDE),
         CHS_EVENT_SMAS_HISTORY_ID = ifelse(CHS_EVENT_SMAS_HISTORY_ID %in% "LAB_INTERNAL", "00-QAQC-0.0", CHS_EVENT_SMAS_HISTORY_ID),
         CHS_EVENT_SMAS_SAMPLE_DATE = as.Date(CHS_EVENT_SMAS_SAMPLE_DATE, format = "%m/%d/%Y"),
         CHS_EVENT_SMAS_SAMPLE_DATE = format((CHS_EVENT_SMAS_SAMPLE_DATE), "%m/%d/%Y"),
         CHS_SAMPLE_RECEIPT_DATE = as.Date(CHS_SAMPLE_RECEIPT_DATE, format = "%m/%d/%Y"),
         CHS_SAMPLE_RECEIPT_DATE = format((CHS_SAMPLE_RECEIPT_DATE), "%m/%d/%Y"),
         CHS_SAMPLE_DATETIME = as.POSIXct(CHS_SAMPLE_DATETIME, format = "%m/%d/%Y %H:%M:%S"),
         CHS_SAMPLE_DATETIME = format((CHS_SAMPLE_DATETIME), "%m/%d/%Y %H:%M:%S")
         )  

result.all.FINAL <- result.all.FINAL %>% 
  mutate(CHR_ANALYSIS_DATE = as.POSIXct(CHR_ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S"),
         CHR_ANALYSIS_DATE = format((CHR_ANALYSIS_DATE), "%m/%d/%Y %H:%M:%S")
)


# Correct erroneous ALS sample date entries
sample.all.FINAL <- sample.all.FINAL %>% 
  mutate(CHS_EVENT_SMAS_SAMPLE_DATE = ifelse(CHS_SAMPLE_NAME %in% "01-CHAU-0.4-09162020-W-SEQ", "09/16/2020", CHS_EVENT_SMAS_SAMPLE_DATE),
         CHS_SAMPLE_DATETIME = ifelse(CHS_SAMPLE_NAME %in% "01-CHAU-0.4-09162020-W-SEQ", "09/16/2020 10:30:00", CHS_SAMPLE_DATETIME),
         CHS_EVENT_SMAS_SAMPLE_DATE = ifelse(CHS_SAMPLE_NAME %in% "12-MOHK-79.5-06152020-W", "06/15/2020", CHS_EVENT_SMAS_SAMPLE_DATE),
         CHS_SAMPLE_DATETIME = ifelse(CHS_SAMPLE_NAME %in% "12-MOHK-79.5-06152020-W", "06/15/2020 12:00:00", CHS_SAMPLE_DATETIME),
         CHS_EVENT_SMAS_SAMPLE_DATE = ifelse(CHS_SAMPLE_NAME %in% "08-BLCK-84.5-06152020-W", "06/15/2020", CHS_EVENT_SMAS_SAMPLE_DATE),
         CHS_SAMPLE_DATETIME = ifelse(CHS_SAMPLE_NAME %in% "08-BLCK-84.5-06152020-W", "06/15/2020 09:00:00", CHS_SAMPLE_DATETIME)
         )


```


```{r Test table joins}

test.sample.all.FINAL <- sample.all.FINAL %>% 
  rename(SSC = CHS_SYS_SAMPLE_CDE,
         SDG = CHS_SAMPLE_DEL_GRP)
test.result.all.FINAL <- result.all.FINAL %>% 
  rename(SSC = CHR_SYS_SAMPLE_CDE,
         SDG = CHR_SAMPLE_DEL_GRP)

test.sample.result <- left_join(test.sample.all.FINAL, test.result.all.FINAL, by = c("SSC", "SDG")) 
# checks out okay
rm(test.sample.all.FINAL, test.result.all.FINAL, test.sample.result)

```


```{r Test pcode join}

pcode <- read.csv(file.path(datamod.dir, "20201013_S_CHEM_PARAMETER.csv"), stringsAsFactors = FALSE, colClasses = "character") %>% 
  bind_rows(read.csv(file.path(datamod.dir, "20210415_S_CHEM_PARAMETER_2020-append.csv"), stringsAsFactors = FALSE, colClasses = "character"))

test.result.pcode <- result.all.form %>% 
  rename(CHEM_PARAMETER_PCODE = CHR_PCODE) %>% 
  left_join(pcode, by = "CHEM_PARAMETER_PCODE") %>% 
  select(CHEM_PARAMETER_PCODE, CHEM_PARAMETER_NAME, CHR_CHEMICAL_NAME, CHEM_PARAMETER_UNIT_NOSP, CHR_RESULT_UNIT,
         CHEM_PARAMETER_FRACTION, CHR_FRACTION) %>% 
  unique() %>% 
  mutate(CHR_CHEMICAL_NAME_caps = toupper(CHR_CHEMICAL_NAME))

```


```{r Exporting PCB pcode info, eval = FALSE}
#Realized can no longer use 3 general pcodes for PCBs since chemical_name field was removed from RESULT table. Using code below to generate PCB code info and export for appending to pcode table in DB.
# Generate info to export for adding PCBs to pcode tables

pcodes.for.pcbs <- test.result.pcode %>% 
  mutate(CHR_CHEMICAL_NAME_caps = toupper(CHR_CHEMICAL_NAME))

write.table(pcodes.for.pcbs, file = file.path(datamod.dir, "pcodes_for_append_2020-04-15.csv"),sep=",", row.names = FALSE, na = "")

rm(test.result.pcode)
```

```{r Check field names against previous submission}

sample.db <- read.csv(file.path(datamod.dir, "20210129_S_CHEM_HISTORY_SAMPLE.csv"), stringsAsFactors = FALSE) 
result.db <- read.csv(file.path(datamod.dir, "20210129_S_CHEM_HISTORY_RESULT.csv"), stringsAsFactors = FALSE)
sample.db.unique <- lapply(sample.db, unique)
result.db.unique <- lapply

setdiff(colnames(sample.db), colnames(sample.all.FINAL))
setdiff(colnames(sample.all.FINAL), colnames(sample.db))

setdiff(colnames(result.db), colnames(result.all.FINAL))
setdiff(colnames(result.all.FINAL), colnames(result.db))

# Found: All OK!
```


Generate EVENT ID records for Charlie to crosscheck against, and append to survey event IDs
```{r Generate event IDs}
event.id <- sample.all.FINAL %>% 
  distinct(CHS_EVENT_SMAS_HISTORY_ID, CHS_EVENT_SMAS_SAMPLE_DATE)

```


Export tables
```{r Export tables, eval = FALSE}

write.table(event.id, file = file.path(datamod.dir, "20210415_SMAS_chem_2020_event_IDs.csv"),sep=",", row.names = FALSE, na = "")
write.table(sample.all.FINAL, file = file.path(datamod.dir, "20210430_S_CHEM_HISTORY_SAMPLE_2020-append.csv"),sep=",", row.names = FALSE, na = "")
write.table(result.all.FINAL, file = file.path(datamod.dir, "20210415_S_CHEM_HISTORY_RESULT_2020-append.csv"),sep=",", row.names = FALSE, na = "")

```


```{r Create and update MASTER tables}

## Append 2020 to 2001-2019 submitted data

# RESULT
result.hist <- read.csv(file.path(datamod.dir, "historical/20210129_S_CHEM_HISTORY_RESULT.csv"), stringsAsFactors = FALSE) %>% 
  # Filter out 2019 PCB data, which ITS removed from historical data as a result of generic PCB pcodes being removed from pcode table. 
  # Will attach new PCB pcodes to 2019 data and resubmit at a later point.
  filter(!(CHR_PCODE %in% c(167, 168, 169)))
result.2020 <- read.csv(file.path(datamod.dir, "2020/20210415_S_CHEM_HISTORY_RESULT_2020-append.csv"), stringsAsFactors = FALSE)

# Check field differences
# setdiff(colnames(result.hist), colnames(result.2020))
# [1] "CHR_SAMPLE_DEL_GRP_EQUIS" "CHR_LAB_VALIDATION_LEVEL"
# OK. Two missing in 2020 are historical only.

result.master <- result.hist %>% 
  bind_rows(result.2020)

#SAMPLE
sample.hist <- read.csv(file.path(datamod.dir, "historical/20210129_S_CHEM_HISTORY_SAMPLE.csv"), stringsAsFactors = FALSE) %>% 
  filter(!(CHS_SAMPLE_DEL_GRP %in% c("L2261539", "L2332254", "L2375300")))
  # Filter out 2019 PCB data, which ITS removed from historical data as a result of generic PCB pcodes being removed from pcode table. 
  # Will attach new PCB pcodes to 2019 data and resubmit at a later point.
sample.2020 <- read.csv(file.path(datamod.dir, "2020/20210430_S_CHEM_HISTORY_SAMPLE_2020-append.csv"), stringsAsFactors = FALSE)

# Check field differences
# setdiff(colnames(sample.hist), colnames(sample.2020))
# [1] "CHS_SAMPLE_DEL_GRP_EQUIS"
# OK. One missing in 2020 are historical only.

sample.master <- sample.hist %>% 
  bind_rows(sample.2020)

# Chem param table
param.existing <- read.csv(file.path(datamod.dir, "historical/20201013_S_CHEM_PARAMETER.csv"), stringsAsFactors = FALSE) %>% 
  # Filter out 2019 PCB data, which ITS removed from historical data as a result of generic PCB pcodes being removed from pcode table. 
  # Will attach new PCB pcodes to 2019 data and resubmit at a later point.
  filter(!(CHEM_PARAMETER_PCODE %in% c(167, 168, 169)))
param.append <- read.csv(file.path(datamod.dir, "2020/20210415_S_CHEM_PARAMETER_2020-append.csv"), stringsAsFactors = FALSE)

param.master <- param.existing %>% 
  bind_rows(param.append)

write.table(result.master, file = file.path(datamod.dir, "MASTER_S_CHEM_HISTORY_RESULT_2021-05-03.csv"),sep=",", row.names = FALSE, na = "")
write.table(sample.master, file = file.path(datamod.dir, "MASTER_S_CHEM_HISTORY_SAMPLE_2021-05-03.csv"),sep=",", row.names = FALSE, na = "")
write.table(param.master, file = file.path(datamod.dir, "MASTER_S_CHEM_PARAMETER_2021-05-03.csv"),sep=",", row.names = FALSE, na = "")

```

