---
title: "compile_2018_2019"
output: html_document
---

Load in libs, set project dirs
```{r}
library(tidyverse)

root.dir <- rprojroot::find_root("chem_hist_cleaning.Rproj")
target.dir <- file.path(root.dir, "data", "2018-2019_zach_ITS")
qaqc_dir <- file.path(target.dir, "qaqc_output")

raw_dir_2018 <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2018/all_SBU_routine/")
raw_dir_2019 <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2019/all_SBU_Mohawk_Routine_complete/")
raw_dir_2019.pcb <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2019/routine_pcbs/")

```

Import and join bound sample, result, and batch files from raw processing. Perform necessary mutations.
```{r}
sample.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_SAMPLE-SMAS_complete_2020-05-08.csv"))
result.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_RESULT-SMAS_complete_2020-05-08.csv"))
batch.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_BATCH-SMAS_complete_2020-05-08.csv"))

sample.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_SAMPLE-SMAS_complete_2020-05-11.csv"))
result.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_RESULT-SMAS_complete_2020-05-11.csv"))
batch.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_BATCH-SMAS_complete_2020-05-11.csv"))

# Add in PCBs separately (processed raw separately)
sample.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_SAMPLE-EMIL_PCBs_2020-06-22.csv"))
result.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_RESULT-EMIL_PCBs_2020-06-22.csv"), col_types = cols(fraction = col_character())) %>% 
  # mutate(lab_sdg = word(lab_sdg, 3))
  # Correct bad contractor SDG formatting 
  mutate(lab_sdg = sub("R1903399 - L2261539", "L2261539", lab_sdg))
batch.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_BATCH-EMIL_PCBs_2020-06-22.csv"), col_types = cols(fraction = col_character()))

sample.all <- bind_rows(sample.2018, sample.2019, sample.2019.pcb)
result.all <- bind_rows(result.2018, result.2019, result.2019.pcb) %>% 
  rename(sample_delivery_group = lab_sdg)
batch.all <- bind_rows(batch.2018, batch.2019, batch.2019.pcb)

rm(sample.2018, sample.2019, sample.2019.pcb, result.2018, result.2019, result.2019.pcb, batch.2018, batch.2019, batch.2019.pcb)
```

Test join by sys_sample_code and SDG
```{r}
test_join_sample.result <- full_join(sample.all, result.all, by = c("sys_sample_code", "sample_delivery_group"))

# CHECKS OUT OKAY. Same number of records created in joined table as in RESULT table.

rm(test_join_sample.result)
```



Import and bind flags from QAQC output files
```{r}
# Import all qaqc output files in subdir and bind together as a dataframe
setwd(qaqc_dir)
qaqc.output.bound <- list.files(path = qaqc_dir, pattern = "*.csv") %>% 
  map_df(~read_csv(.,  col_types = cols(fraction = col_character()))) %>% 
  mutate(project_name = str_replace(project_name, "RIBS_", "")) %>% 
  mutate(project_name = str_replace(project_name, " - ", "_")) %>% 
  mutate(project_name = str_replace(project_name, "_-_", "_")) %>% 
  mutate(project_name = str_replace_all(project_name, " ", "_")) %>% 
  mutate(chemical_name = tolower(chemical_name))

qaqc.output.bound <- qaqc.output.bound %>%
  select(project_name, sys_sample_code, sample_delivery_group, chemical_name, fraction, validator_qualifiers, interpreted_qualifiers, qaqc_date) %>%
  filter(chemical_name != "selenium") %>% 
  mutate(validated_yn = "Y") %>% 
  rename(VALIDATOR_QUAL_EXPLN = interpreted_qualifiers)
# Ignore selenium flags (erroneously reported by ALS; already removed from RESULT file)

```


Join flags and related fields to results table
```{r}
result.all <- result.all %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  select(-validated_yn, -validator_qualifiers)

# Test various joins and compare to identify possible issues
result.all.flags.left <- left_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.all.flags.full <- full_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# Resulting left and full joins are identical (no recs left behind)

result.all.flags.inner <- inner_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# matches number of QAQC records in chunk above (all have match)

# Do antijoin to make sure non-joined records are all lab and QC samples.
result.all.flags.anti <- anti_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.sample.anti <- right_join(sample.all, result.all.flags.anti, by = c("sys_sample_code", "sample_delivery_group"))

# filter to non-lab and QC samples to verify what's missing was intentional (Ausable, Qaussaic, Duane Lake, PCBs)

result.sample.anti.sub <- result.sample.anti %>% 
  filter(sample_type_code %in% "N",
         DEC_sample_type %in% "N") 

# > sort(unique(result.sample.anti.sub$SITE_ID))
#  [1] "03-EMIL-5.1"       "10-CHUB-5.0"       "10-CHUB_T4-0.6"    "10-CHUB_T4-0.7"    "10-NMOW_T1-1.7"    "10-NMOW_T1-1.8"    "10-SABL_W-10.3"    "10-SABL_W-12.9"    "10-SABL_W-15.1"   
# [10] "10-SABL_W-18.6"    "10-SABL_W-20.7"    "10-SABL_W_T13-0.1" "10-SABL_W_T13-0.2" "10-SABL_W_T14-0.2" "10-SABL_W_T14-0.3" "10-SABL_W_T26-0.1" "10-SABL_W_T26-0.2" "10-SABL_W_T27-0.1"
# [19] "10-SABL_W_T27-0.2" "11-UHUD-2.7"       "12-LDUAN_T1-0.1"   "12-MOHK-1.5"       "12-MOHK-13.4"      "12-MOHK-17.3"      "12-MOHK-24.0"      "13-WQUAS-9.8"   

# All above sites are PCBs, Ausable, Duane Lake. Mohawk sites present are likely DBP surrogate parameters that we don't flag and don't need to retain. Double checking this below.

result.sample.anti.sub.mohk <- result.sample.anti.sub %>% 
  filter(grepl("MOHK|UHUD", SITE_ID))

# > unique(result.sample.anti.sub.mohk$chemical_name)
# [1] "p-bromofluorobenzene"                        "dibromofluoromethane"                        "toluene-d8"                                  "2,3-dibromopropionic acid"                  
# [5] "1-bromo-4-fluorobenzene bromofluorobenzene)"
# Confirmed, above are DBP surrograte params that we do not flag.

#  Look for duplicate records (possible issues with join)
dups <- result.all.flags.full %>% 
  group_by(sys_sample_code, sample_delivery_group, chemical_name, fraction) %>% 
  mutate(dups = n()) %>% 
  filter(dups > 1)
 # Only dups present are with PCBs and they are present in the raw EDDs.

# Clean up dataframes and rename
result.all <- result.all.flags.full
rm(qaqc.output.bound, result.all.flags.left, result.all.flags.full, result.all.flags.inner, result.all.flags.anti, result.sample.anti, result.sample.anti.sub, result.sample.anti.sub.mohk, dups)

```

Flag any field results not run through QAQC (Duane Lake, Quassiac Creek, Ausable 2018)
```{r}
# Join sample type field from SAMPLE table to gather required info for filtering
sample.all.type <- sample.all %>% 
  select(SITE_ID, sys_sample_code, sample_source, sample_delivery_group, DEC_sample_type, sample_type_code)
result.all.type <- left_join(result.all, sample.all.type, by = c("sys_sample_code", "sample_delivery_group")) %>% 
  # select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, validator_qualifiers, VALIDATOR_QUAL_EXPLN, everything())
  select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, everything())

# Check what types of samples got flags
result.all.type.check <- result.all.type %>% 
  select(validator_qualifiers, DEC_sample_type) %>% 
  distinct()

# Filter out normal samples that didn't get flags to verify that only the ones intentionally not flagged are there.
result.all.notflagged.n <- result.all.type %>% 
  filter(is.na(validator_qualifiers),
         DEC_sample_type %in% "N",
         sample_source %in% "Field")

# List output below as expected. EMIL and MOHWK sites had parameters that we don't flag, and the remaining are sites from projects with QAQC errors or insufficient QAQC samples were collected.
# > sort(unique(result.all.notflagged.n$SITE_ID))
#  [1] "03-EMIL-5.1"       "10-CHUB-5.0"       "10-CHUB_T4-0.6"    "10-CHUB_T4-0.7"    "10-NMOW_T1-1.7"    "10-NMOW_T1-1.8"    "10-SABL_W-10.3"    "10-SABL_W-12.9"    "10-SABL_W-15.1"   
# [10] "10-SABL_W-18.6"    "10-SABL_W-20.7"    "10-SABL_W_T13-0.1" "10-SABL_W_T13-0.2" "10-SABL_W_T14-0.2" "10-SABL_W_T14-0.3" "10-SABL_W_T26-0.1" "10-SABL_W_T26-0.2" "10-SABL_W_T27-0.1"
# [19] "10-SABL_W_T27-0.2" "11-UHUD-2.7"       "12-LDUAN_T1-0.1"   "12-MOHK-1.5"       "12-MOHK-13.4"      "12-MOHK-17.3"      "12-MOHK-24.0"      "13-WQUAS-9.8"   

# Add NF flags and explanations to all those above except EMIL and MOHK sites
result.all.flagged2 <- result.all.type %>% 
  mutate(validator_qualifiers = ifelse(
    is.na(validator_qualifiers) &
      DEC_sample_type %in% "N" &
      sample_source %in% "Field" &
      !grepl("*EMIL", SITE_ID) &
      !grepl("*MOHK", SITE_ID), 
    "NF", validator_qualifiers)) %>% 
  mutate(VALIDATOR_QUAL_EXPLN = ifelse(validator_qualifiers %in% "NF", 
    "Not flagged due to QAQC error or insufficient QAQC sampling", VALIDATOR_QUAL_EXPLN))  

# Veryify that only remaining field "N" samples without flags are those params we don't flag (PCBs and 5 DBP surrogate params)
result.all.flagged2.naflags <- result.all.flagged2 %>% 
  filter(is.na(validator_qualifiers),
         sample_source %in% "Field",
         DEC_sample_type %in% "N")
# Above checks out :)

# Clean up new result table and remove joined fields
result.all.flagged2 <- result.all.flagged2 %>% 
  # select(everything(), validator_qualifiers, VALIDATOR_QUAL_EXPLN, qaqc_date, validated_yn) %>% 
  select(-SITE_ID, -sample_source, -DEC_sample_type, -sample_type_code) 

rm(sample.all.type, result.all.type, result.all.type.check, result.all.notflagged.n, result.all.flagged2.naflags)


```


Join pcodes field using "pcode join table" (based on chemical_name, fraction, and unit)
```{r}

# Import pcodes 
pcode_path <- file.path("C:/Users/gmlemley/New York State Office of Information Technology Services/SMAS - Streams Data Modernization/to_be_cleaned/chem_parameters")
pcode.join <- readxl::read_excel(file.path(pcode_path, "pcode_join_table_CLEAN_2020-06-25.xlsx")) %>% 
  select(RESULT_TYPE, everything()) %>% 
  select(-"Has duplicate", -"Notes") %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  mutate(result_unit = tolower(result_unit)) %>% 
  mutate(DEC_pcode_FINAL = formatC(DEC_pcode_FINAL, width = 3, format = "d", flag = "0")) %>% 
  # Remove instances of duplicate rows that represented differing unit capitalization (will just do this in the data) 
  distinct()

# Export cleaned pcode table for sending to LMAS
# write.csv(pcode.join, file.path(root.dir, "parameters", "dec_pcode_join_2020-08-24.csv"), row.names = FALSE)

# Filter to lab only for joining to chem data
pcode.join.lab <- pcode.join %>% 
  filter(RESULT_TYPE %in% "lab") %>%
  select(-RESULT_TYPE)

# Join to chem results table
result.pcodes <- left_join(result.all.flagged2, pcode.join.lab, by = c("chemical_name", "fraction", "result_unit")) %>% 
  select(DEC_pcode_FINAL, chemical_name, everything())

# Review records that didn't get pcodes assigned
result.pcodes.na <- result.pcodes %>% 
  filter(is.na(DEC_pcode_FINAL))
rm(result.pcodes.na)

# Populate missing pcodes (PCBs)
result.pcodes <- result.pcodes %>% 
  mutate(DEC_pcode_FINAL = ifelse(is.na(DEC_pcode_FINAL) & result_unit %in% "pg/l", 168, DEC_pcode_FINAL)) %>% 
  mutate(DEC_pcode_FINAL = ifelse(is.na(DEC_pcode_FINAL) & result_unit %in% "percent", 169, DEC_pcode_FINAL))

# summarize join for review  
result.pcodes.check <- result.pcodes %>% 
  select(DEC_pcode_FINAL, chemical_name, fraction, result_unit) %>% 
  distinct()

rm(pcode.join, pcode.join.lab, result.all.flagged2)


```



Fix bad dates from ALS
```{r}
# Correct bad years in sample_date and analysis_date fields (for just a handful lab QC samples of TDS and chlorophyll-a results)

# Sample dates in SAMPLE file
# Analysis dates in RESULT and BATCH files
# 1999-08-07 should be ...
# 2016-06-16 sould be ...

# Find bad years
sample.all.form.datecheck <- sample.all %>% 
  filter(!grepl("*2018", sample_date)) %>% 
  filter(!grepl("*2019", sample_date))

# Test mutation
sample.all.form.datecheck <- sample.all.form.datecheck %>% 
  mutate(sample_date = str_replace(sample_date, "1999", "2019")) %>% 
  mutate(sample_date = str_replace(sample_date, "2016", "2019"))

# Perform mutation
sample.all.corr <- sample.all %>% 
  mutate(sample_date = str_replace(sample_date, "1999", "2019")) %>% 
  mutate(sample_date = str_replace(sample_date, "2016", "2019"))

rm(sample.all.form.datecheck)





##### COMPLETE FOR BATCH AND RESULT #### (analysis date too)










```


Reformat field names and add blank fields
```{r}

sample.all.form <- sample.all.corr %>%
  rename_all(toupper) %>%
  rename(
    SITE_HISTORY_ID = SITE_ID,
    DEC_SAMPLE_TYPE_CDE = DEC_SAMPLE_TYPE,
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    SAMPLE_MATRIX_CDE = SAMPLE_MATRIX_CODE,
    LAB_SAMPLE_TYPE_CDE = SAMPLE_TYPE_CODE,
    PARENT_SAMPLE_CDE = PARENT_SAMPLE_CODE,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP,
    SYS_LOC_CDE = SYS_LOC_CODE,
    WTR_SAMPLE_DATETIME = SAMPLE_DATE
  ) %>%
  mutate(WTR_SAMPLE_DATETIME.posixct = as.POSIXct(WTR_SAMPLE_DATETIME, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(SAMPLE_DATE = strftime(WTR_SAMPLE_DATETIME.posixct, "%m/%d/%Y")) %>%
  rename_all(function(x)
    paste0("CHS_", x))
# mutate(EVENT_SMAS_ID = paste0(CHS_SITE_ID,"_",EVENT_ID_DATE))

result.all.form <- result.all %>%
  rename_all(toupper) %>%
  #### MAKE ALL CHEMICAL_NAMEs UPPERCASE ###
  rename(
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME,
    LAB_MATRIX_CDE = LAB_MATRIX_CODE,
    LAB_NAME_CDE = LAB_NAME_CODE,
    SUBSAMPLE_AMT = SUBSAMPLE_AMOUNT,
    SUBSAMPLE_AMT_UNIT = SUBSAMPLE_AMOUNT_UNIT,
    RESULT_TYPE_CDE = RESULT_TYPE_CODE,
    REPORTABLE_RESULT_IND = REPORTABLE_RESULT,
    LAB_QUAL = LAB_QUALIFIERS,
    VALIDATOR_QUAL = VALIDATOR_QUALIFIERS,
    INTERPRETED_QUAL = INTERPRETED_QUALIFIERS,
    VALIDATED_IND = VALIDATED_YN,
    METHOD_DETECT_LIMIT = METHOD_DETECTION_LIMIT,
    REPORTING_DETECT_LIMIT = REPORTING_DETECTION_LIMIT,
    QC_ORIG_CONC = QC_ORIGINAL_CONC,
    QC_DUP_ORIG_CONC = QC_DUP_ORIGINAL_CONC,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP
  ) %>%
  mutate(
    VALIDATOR_QUAL_REASON_CDE = "",
    VALIDATOR_SAMPLE_ACCURACY = "",
    VALIDATOR_SAMPLE_PRECISION_FIELD = "",
    VALIDATOR_SAMPLE_PRECISION_LAB = "",
    VALIDATOR_SAMPLE_EQUIP_BLANK = "",
    VALIDATOR_SAMPLE_PARAM_PAIR = "",
    VALIDATOR_QUAL_EXPLN = "",
    VALIDATION_DATE = "",
    LAB_VALIDATION_LEVEL = NA
  ) %>%
  # mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  # mutate(PREP_DATE = as.POSIXct(PREP_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(FRACTION = case_when(
    FRACTION == "T" ~ "TOTAL",
    FRACTION == "D" ~ "DISSOLVED",
    TRUE ~ FRACTION)) %>% 
  rename_all(function(x)
    paste0("CHR_", x)) %>%
  mutate(
    CHEM_HISTORY_RESULT_ID = "",
    CHEM_HISTORY_SAMPLE_ID = "",
    CHEM_PARAMETER_ID = "",
    CREATE_DATE = "",
    END_DATE = "",
    UPDATE_DATE = "",
    UPDATED_BY_GUID = ""
  )

batch.all.form <- batch.all %>%
  rename_all(toupper) %>%
  rename(SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
         LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME) %>%
  # mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(FRACTION = case_when(
    FRACTION == "T" ~ "TOTAL",
    FRACTION == "D" ~ "DISSOLVED",
    TRUE ~ FRACTION)) %>% 
  rename_all(function(x)
    paste0("CHB_", x))

```


Select final headers as per ITS data model (copied from compile_2017-2019.Rmd)
```{r}
# Headers selections below copied directly from the data dictionary, 3/27/20.

# SAMPLE table
sample.all.FINAL <- sample.all.form %>% 
    select(CHS_SITE_HISTORY_ID, CHS_SAMPLE_DATE, CHS_SITE_ID_CORR_IND, CHS_DATA_PROVIDER, CHS_SYS_SAMPLE_CDE, 
           CHS_SAMPLE_NAME, CHS_SAMPLE_MATRIX_CDE, CHS_DEC_SAMPLE_TYPE_CDE, CHS_LAB_SAMPLE_TYPE_CDE, CHS_SAMPLE_SOURCE, 
           CHS_PARENT_SAMPLE_CDE, CHS_SAMPLE_DEL_GRP, CHS_WTR_SAMPLE_DATETIME, CHS_SAMPLE_RECEIPT_DATE, CHS_SYS_LOC_CDE,
           CHS_CHAIN_OF_CUSTODY, CHS_SAMPLER, CHS_SAMPLING_COMPANY_CODE, CHS_COMMENT)

# RESULT table
result.all.FINAL <- result.all.form %>% 
    select(CHEM_HISTORY_RESULT_ID, CHEM_HISTORY_SAMPLE_ID, CHEM_PARAMETER_ID, CHR_SYS_SAMPLE_CDE, CHR_LAB_ANAL_METHOD_NAME,
           CHR_ANALYSIS_DATE, CHR_FRACTION, CHR_TEST_TYPE, CHR_LAB_MATRIX_CDE, CHR_DILUTION_FACTOR, CHR_PREP_METHOD, 
           CHR_PREP_DATE, CHR_LAB_NAME_CDE, CHR_QC_LEVEL, CHR_LAB_SAMPLE_ID, CHR_SUBSAMPLE_AMT, 
           CHR_SUBSAMPLE_AMT_UNIT, CHR_FINAL_VOLUME, CHR_FINAL_VOLUME_UNIT, CHR_CAS_RN, CHR_CHEMICAL_NAME, CHR_RESULT_VALUE, 
           CHR_RESULT_UNIT, CHR_RESULT_TYPE_CDE, CHR_REPORTABLE_RESULT_IND, CHR_DETECT_FLAG, CHR_LAB_QUAL, CHR_INTERPRETED_QUAL, 
           CHR_VALIDATED_IND, CHR_VALIDATOR_QUAL, CHR_VALIDATOR_QUAL_EXPLN, CHR_VALIDATOR_QUAL_REASON_CDE, CHR_VALIDATION_DATE, 
           CHR_VALIDATOR_SAMPLE_ACCURACY, CHR_VALIDATOR_SAMPLE_PRECISION_FIELD, CHR_VALIDATOR_SAMPLE_PRECISION_LAB, 
           CHR_VALIDATOR_SAMPLE_EQUIP_BLANK, CHR_VALIDATOR_SAMPLE_PARAM_PAIR, CHR_METHOD_DETECT_LIMIT, CHR_REPORTING_DETECT_LIMIT, 
           CHR_QUANTITATION_LIMIT, CHR_DETECTION_LIMIT_UNIT, CHR_VALIDATION_LEVEL, CHR_RESULT_COMMENT, CHR_QC_ORIG_CONC, 
           CHR_QC_SPIKE_ADDED, CHR_QC_SPIKE_MEASURED, CHR_QC_SPIKE_RECOVERY, CHR_QC_DUP_ORIG_CONC, CHR_QC_DUP_SPIKE_ADDED, 
           CHR_QC_DUP_SPIKE_MEASURED, CHR_QC_DUP_SPIKE_RECOVERY, CHR_QC_RPD, CHR_QC_SPIKE_LCL, CHR_QC_SPIKE_UCL, CHR_QC_RPD_CL, 
           CHR_QC_SPIKE_STATUS, CHR_QC_DUP_SPIKE_STATUS, CHR_QC_RPD_STATUS, CHR_SAMPLE_DEL_GRP)

# BATCH table
batch.all.FINAL <- batch.all.form %>% 
    select(CHB_SYS_SAMPLE_CDE, CHB_LAB_ANAL_METHOD_NAME, CHB_ANALYSIS_DATE, 
           CHB_FRACTION, CHB_TEST_TYPE, CHB_TEST_BATCH_TYPE, CHB_TEST_BATCH_ID)

```

Modify data further as needed to meet ITS submission guidelines
```{r}
# library(datetime)
# 
# sample.all.form <- sample.all.form %>%
#   mutate(CHS_SAMPLE_DATE = as.POSIXct(CHS_SAMPLE_DATE, format = "%m/%d/%Y %H:%M:%S"),
#          CHS_SAMPLE_DATE_2 = format((CHS_SAMPLE_DATE), "%m/%d/%Y %H:%M:%S"),
#          CHS_SAMPLE_RECEIPT_DATE = as.Date(CHS_SAMPLE_RECEIPT_DATE, format = "%m/%d/%Y"),
#          CHS_SAMPLE_RECEIPT_DATE_2 = format((CHS_SAMPLE_RECEIPT_DATE), "%m/%d/%Y"))

# Not needed since data comes in the format that ITS (Cindy) is requesting. Retain above code for future reference when similar formatting is needed.

```

Replace all NA as blanks (run this???)
```{r}




sample.all.FINAL.noNA <- sample.all.FINAL %>%
  replace(is.na(.), "")
# result.all.FINAL.noNA <- result.all.FINAL %>% 
#   replace(is.na(.), "")
# batch.all.FINAL.noNA <- batch.all.FINAL %>% 
#   replace(is.na(.), "")





```



Export 2018-2019 chem tables 
```{r}

write.table(sample.all.FINAL.noNA, file = file.path(root.dir, "data", "2018-2019_ITS_2020-08-25", "S_CHEM_HISTORY_SAMPLE.csv"),sep=",", row.names = FALSE)
write.table(result.all.FINAL.noNA, file = file.path(root.dir, "data", "2018-2019_ITS_2020-08-25", "S_CHEM_HISTORY_RESULT.csv"),sep=",", row.names = FALSE)
write.table(batch.all.FINAL.noNA, file = file.path(root.dir, "data", "2018-2019_ITS_2020-08-25", "S_CHEM_HISTORY_BATCH.csv"),sep=",", row.names = FALSE)

```


Import final pcode table and reformat for ITS submission
```{r}

```


