---
title: "compile_2018_2019"
output: html_document
---

Load in libs, set project dirs
```{r}
library(tidyverse)

root.dir <- rprojroot::find_root("chem_hist_cleaning.Rproj")
target.dir <- file.path(root.dir, "data", "2018-2019_zach_ITS")
qaqc_dir <- file.path(target.dir, "qaqc_output")

raw_dir_2018 <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2018/all_SBU_routine/")
raw_dir_2019 <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2019/all_SBU_Mohawk_Routine_complete/")
raw_dir_2019.pcb <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2019/routine_pcbs/")

```

Import and join bound sample, result, and batch files from raw processing. Perform necessary mutations.
```{r}
sample.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_SAMPLE-SMAS_complete_2020-05-08.csv"))
result.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_RESULT-SMAS_complete_2020-05-08.csv"))
batch.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_BATCH-SMAS_complete_2020-05-08.csv"))

sample.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_SAMPLE-SMAS_complete_2020-05-11.csv"))
result.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_RESULT-SMAS_complete_2020-05-11.csv"))
batch.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_BATCH-SMAS_complete_2020-05-11.csv"))

# Add in PCBs separately (processed raw separately)
sample.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_SAMPLE-EMIL_PCBs_2020-06-22.csv"))
result.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_RESULT-EMIL_PCBs_2020-06-22.csv"), col_types = cols(fraction = col_character())) %>% 
  # mutate(lab_sdg = word(lab_sdg, 3))
  # Correct bad contractor SDG formatting 
  mutate(lab_sdg = sub("R1903399 - L2261539", "L2261539", lab_sdg))
batch.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_BATCH-EMIL_PCBs_2020-06-22.csv"), col_types = cols(fraction = col_character()))

sample.all <- bind_rows(sample.2018, sample.2019, sample.2019.pcb)
result.all <- bind_rows(result.2018, result.2019, result.2019.pcb) %>% 
  rename(sample_delivery_group = lab_sdg)
batch.all <- bind_rows(batch.2018, batch.2019, batch.2019.pcb)

rm(sample.2018, sample.2019, sample.2019.pcb, result.2018, result.2019, result.2019.pcb, batch.2018, batch.2019, batch.2019.pcb)
```

Test join by sys_sample_code and SDG
```{r}
test_join_sample.result <- full_join(sample.all, result.all, by = c("sys_sample_code", "sample_delivery_group"))

# CHECKS OUT OKAY. Same number of records created in joined table as in RESULT table.

rm(test_join_sample.result)
```



Import and bind flags from QAQC output files
```{r}
# Import all qaqc output files in subdir and bind together as a dataframe
setwd(qaqc_dir)
qaqc.output.bound <- list.files(path = qaqc_dir, pattern = "*.csv") %>% 
  map_df(~read_csv(.,  col_types = cols(fraction = col_character()))) %>% 
  mutate(project_name = str_replace(project_name, "RIBS_", "")) %>% 
  mutate(project_name = str_replace(project_name, " - ", "_")) %>% 
  mutate(project_name = str_replace(project_name, "_-_", "_")) %>% 
  mutate(project_name = str_replace_all(project_name, " ", "_")) %>% 
  mutate(chemical_name = tolower(chemical_name))

qaqc.output.bound <- qaqc.output.bound %>%
  select(project_name, sys_sample_code, sample_delivery_group, chemical_name, fraction, validator_qualifiers, interpreted_qualifiers, qaqc_date) %>%
  filter(chemical_name != "selenium")

```


Join flags and related fields to results table
```{r}
result.all <- result.all %>% 
  mutate(chemical_name = tolower(chemical_name))


# Test various joins and compare to identify possible issues
result.all.flags.left <- left_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.all.flags.full <- full_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# Resulting left and full joins are identical (no recs left behind)

result.all.flags.inner <- inner_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# matches number of QAQC records in chunk above (all have match)

result.all.flags.anti <- anti_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.sample.anti <- right_join(sample.all, result.all.flags.anti, by = c("sys_sample_code", "sample_delivery_group"))

result.sample.full <- full_join(sample.all, result.all.flags.full, by = c("sys_sample_code", "sample_delivery_group"))


dups <- result.sample.full %>% 
  group_by(sys_sample_code, sample_delivery_group, chemical_name, fraction) %>% 
  mutate(dups = n()) %>% 
  filter(dups > 1)
```


Join pcodes field using "pcode join table" (based on chemical_name, fraction, and unit)
```{r}




```



Reformat field names and add blank fields
```{r}

# REMOVE PROJECT NAME FIELD

sample.all.form <- sample.all %>%
  rename_all(toupper) %>%
  rename(
    SITE_HISTORY_ID = SITE_ID,
    DEC_SAMPLE_TYPE_CDE = DEC_SAMPLE_TYPE,
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    SAMPLE_MATRIX_CDE = SAMPLE_MATRIX_CODE,
    LAB_SAMPLE_TYPE_CDE = SAMPLE_TYPE_CODE,
    PARENT_SAMPLE_CDE = PARENT_SAMPLE_CODE,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP
  ) %>%
  rename_all(function(x)
    paste0("CHS_", x))
# mutate(EVENT_ID_DATE = strftime(CHS_SAMPLE_DATE, "%Y%m%d")) %>%
# mutate(EVENT_SMAS_ID = paste0(CHS_SITE_ID,"_",EVENT_ID_DATE))

result.all.form <- result.all %>%
  rename_all(toupper) %>%
  #### MAKE ALL CHEMICAL_NAMEs UPPERCASE ###
  rename(
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME,
    LAB_MATRIX_CDE = LAB_MATRIX_CODE,
    LAB_NAME_CDE = LAB_NAME_CODE,
    SUBSAMPLE_AMT = SUBSAMPLE_AMOUNT,
    SUBSAMPLE_AMT_UNIT = SUBSAMPLE_AMOUNT_UNIT,
    RESULT_TYPE_CDE = RESULT_TYPE_CODE,
    REPORTABLE_RESULT_IND = REPORTABLE_RESULT,
    LAB_QUAL = LAB_QUALIFIERS,
    VALIDATOR_QUAL = VALIDATOR_QUALIFIERS,
    INTERPRETED_QUAL = INTERPRETED_QUALIFIERS,
    VALIDATED_IND = VALIDATED_YN,
    METHOD_DETECT_LIMIT = METHOD_DETECTION_LIMIT,
    REPORTING_DETECT_LIMIT = REPORTING_DETECTION_LIMIT,
    QC_ORIG_CONC = QC_ORIGINAL_CONC,
    QC_DUP_ORIG_CONC = QC_DUP_ORIGINAL_CONC,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP
  ) %>%
  mutate(
    VALIDATOR_QUAL_REASON_CDE = "",
    VALIDATOR_SAMPLE_ACCURACY = "",
    VALIDATOR_SAMPLE_PRECISION_FIELD = "",
    VALIDATOR_SAMPLE_PRECISION_LAB = "",
    VALIDATOR_SAMPLE_EQUIP_BLANK = "",
    VALIDATOR_SAMPLE_PARAM_PAIR = "",
    VALIDATOR_QUAL_EXPLN = "",
    VALIDATION_DATE = "",
    LAB_VALIDATION_LEVEL = NA
  ) %>%
  mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(PREP_DATE = as.POSIXct(PREP_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  rename_all(function(x)
    paste0("CHR_", x)) %>%
  mutate(
    CHEM_HISTORY_RESULT_ID = "",
    CHEM_HISTORY_SAMPLE_ID = "",
    CHEM_PARAMETER_ID = "",
    CREATE_DATE = "",
    END_DATE = "",
    UPDATE_DATE = "",
    UPDATED_BY_GUID = ""
  )

batch.all.form <- batch.all %>%
  rename_all(toupper) %>%
  rename(SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
         LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME) %>%
  mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  rename_all(function(x)
    paste0("CHB_", x)) %>%
  mutate(
    CHEM_HISTORY_BATCH_ID = "",
    CHEM_HISTORY_SAMPLE_ID = "",
    CREATE_DATE = "",
    END_DATE = "",
    UPDATE_DATE = "",
    UPDATED_BY_GUID = ""
  )

```

Select final headers as per ITS data model (copied from compile_2017-2019.Rmd)
```{r}
# Headers selections below copied directly from the data dictionary, 3/27/20.

# SAMPLE table
sample.all.FINAL <- sample.all.form %>% 
    select(EVENT_SMAS_ID, CHS_SITE_ID, CHS_SITE_HISTORY_ID_CORR_IND, CHS_DATA_PROVIDER, CHS_SYS_SAMPLE_CDE, 
           CHS_SAMPLE_NAME, CHS_SAMPLE_MATRIX_CDE, CHS_DEC_SAMPLE_TYPE_CDE, CHS_LAB_SAMPLE_TYPE_CDE, CHS_SAMPLE_SOURCE, 
           CHS_PARENT_SAMPLE_CDE, CHS_SAMPLE_DEL_GRP, CHS_SAMPLE_DATE, CHS_SAMPLE_RECEIPT_DATE,
           CHS_SAMPLER, CHS_SAMPLING_COMPANY_CODE, CHS_COMMENT)

# RESULT table
result.all.FINAL <- result.all.form %>% 
    select(CHEM_HISTORY_RESULT_ID, CHEM_HISTORY_SAMPLE_ID, CHEM_PARAMETER_ID, CHR_SYS_SAMPLE_CDE, CHR_LAB_ANAL_METHOD_NAME,
           CHR_ANALYSIS_DATE, CHR_FRACTION, CHR_TEST_TYPE, CHR_LAB_MATRIX_CDE, CHR_DILUTION_FACTOR, CHR_PREP_METHOD, 
           CHR_PREP_DATE, CHR_LAB_NAME_CDE, CHR_QC_LEVEL, CHR_LAB_SAMPLE_ID, CHR_SUBSAMPLE_AMT, 
           CHR_SUBSAMPLE_AMT_UNIT, CHR_FINAL_VOLUME, CHR_FINAL_VOLUME_UNIT, CHR_CAS_RN, CHR_CHEMICAL_NAME, CHR_RESULT_VALUE, 
           CHR_RESULT_UNIT, CHR_RESULT_TYPE_CDE, CHR_REPORTABLE_RESULT_IND, CHR_DETECT_FLAG, CHR_LAB_QUAL, CHR_INTERPRETED_QUAL, 
           CHR_VALIDATED_IND, CHR_VALIDATOR_QUAL, CHR_VALIDATOR_QUAL_EXPLN, CHR_VALIDATOR_QUAL_REASON_CDE, CHR_VALIDATION_DATE, 
           CHR_VALIDATOR_SAMPLE_ACCURACY, CHR_VALIDATOR_SAMPLE_PRECISION_FIELD, CHR_VALIDATOR_SAMPLE_PRECISION_LAB, 
           CHR_VALIDATOR_SAMPLE_EQUIP_BLANK, CHR_VALIDATOR_SAMPLE_PARAM_PAIR, CHR_METHOD_DETECT_LIMIT, CHR_REPORTING_DETECT_LIMIT, 
           CHR_QUANTITATION_LIMIT, CHR_DETECTION_LIMIT_UNIT, CHR_VALIDATION_LEVEL, CHR_RESULT_COMMENT, CHR_QC_ORIG_CONC, 
           CHR_QC_SPIKE_ADDED, CHR_QC_SPIKE_MEASURED, CHR_QC_SPIKE_RECOVERY, CHR_QC_DUP_ORIG_CONC, CHR_QC_DUP_SPIKE_ADDED, 
           CHR_QC_DUP_SPIKE_MEASURED, CHR_QC_DUP_SPIKE_RECOVERY, CHR_QC_RPD, CHR_QC_SPIKE_LCL, CHR_QC_SPIKE_UCL, CHR_QC_RPD_CL, 
           CHR_QC_SPIKE_STATUS, CHR_QC_DUP_SPIKE_STATUS, CHR_QC_RPD_STATUS, CHR_SAMPLE_DEL_GRP)

# BATCH table
batch.all.FINAL <- batch.all.form %>% 
    select(CHEM_HISTORY_BATCH_ID, CHEM_HISTORY_SAMPLE_ID, CHB_SYS_SAMPLE_CDE, CHB_LAB_ANAL_METHOD_NAME, CHB_ANALYSIS_DATE, 
           CHB_FRACTION, CHB_TEST_TYPE, CHB_TEST_BATCH_TYPE, CHB_TEST_BATCH_ID)

```

Modify data as needed to meet ITS submission guidelines
```{r}
library(datetime)

sample.all.form <- sample.all.form %>%
  mutate(CHS_SAMPLE_DATE = as.POSIXct(CHS_SAMPLE_DATE, format = "%m/%d/%Y %H:%M:%S"),
         CHS_SAMPLE_DATE_2 = format((CHS_SAMPLE_DATE), "%m/%d/%Y %H:%M:%S"),
         CHS_SAMPLE_RECEIPT_DATE = as.Date(CHS_SAMPLE_RECEIPT_DATE, format = "%m/%d/%Y"))



```



Export data (copied from compile_2017-2019.Rmd)
```{r}

write.table(sample.all.FINAL, file= paste0(output.path,"/",output.filename.sample),sep=",", row.names = FALSE)
write.table(result.all.FINAL, file= paste0(output.path,"/",output.filename.result),sep=",", row.names = FALSE)
write.table(batch.all.FINAL, file= paste0(output.path,"/",output.filename.batch),sep=",", row.names = FALSE)

```




