---
title: "compile_2018_2019"
output: html_document
---

Load in libs, set project dirs
```{r}
library(tidyverse)

root.dir <- rprojroot::find_root("chem_hist_cleaning.Rproj")
target.dir <- file.path(root.dir, "data", "2018-2019_zach_ITS")
qaqc_dir <- file.path(target.dir, "qaqc_output")

raw_dir_2018 <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2018/all_SBU_routine/")
raw_dir_2019 <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2019/all_SBU_Mohawk_Routine_complete/")
raw_dir_2019.pcb <- file.path("C:/Data/RIBS/Chem_raw_processing/data_output/2019/routine_pcbs/")

```

Import and join bound sample, result, and batch files from raw processing. Perform necessary mutations.
```{r}
sample.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_SAMPLE-SMAS_complete_2020-05-08.csv"))
result.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_RESULT-SMAS_complete_2020-05-08.csv"))
batch.2018 <- read_csv(file.path(raw_dir_2018, "2018_chem_preqaqc_BATCH-SMAS_complete_2020-05-08.csv"))

sample.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_SAMPLE-SMAS_complete_2020-05-11.csv"))
result.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_RESULT-SMAS_complete_2020-05-11.csv"))
batch.2019 <- read_csv(file.path(raw_dir_2019, "2019_chem_preqaqc_BATCH-SMAS_complete_2020-05-11.csv"))

# Add in PCBs separately (processed raw separately)
sample.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_SAMPLE-EMIL_PCBs_2020-06-22.csv"))
result.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_RESULT-EMIL_PCBs_2020-06-22.csv"), col_types = cols(fraction = col_character())) %>% 
  # mutate(lab_sdg = word(lab_sdg, 3))
  # Correct bad contractor SDG formatting 
  mutate(lab_sdg = sub("R1903399 - L2261539", "L2261539", lab_sdg))
batch.2019.pcb <- read_csv(file.path(raw_dir_2019.pcb, "2019_chem_preqaqc_BATCH-EMIL_PCBs_2020-06-22.csv"), col_types = cols(fraction = col_character()))

sample.all <- bind_rows(sample.2018, sample.2019, sample.2019.pcb)
result.all <- bind_rows(result.2018, result.2019, result.2019.pcb) %>% 
  rename(sample_delivery_group = lab_sdg)
batch.all <- bind_rows(batch.2018, batch.2019, batch.2019.pcb)

rm(sample.2018, sample.2019, sample.2019.pcb, result.2018, result.2019, result.2019.pcb, batch.2018, batch.2019, batch.2019.pcb)
```

Test join by sys_sample_code and SDG
```{r}
test_join_sample.result <- full_join(sample.all, result.all, by = c("sys_sample_code", "sample_delivery_group"))

# CHECKS OUT OKAY. Same number of records created in joined table as in RESULT table.

rm(test_join_sample.result)
```

Import and bind flags from QAQC output files
```{r}
# Import all qaqc output files in subdir and bind together as a dataframe
setwd(qaqc_dir)
qaqc.output.bound <- list.files(path = qaqc_dir, pattern = "*.csv") %>% 
  map_df(~read_csv(.,  col_types = cols(fraction = col_character()))) %>% 
  mutate(project_name = str_replace(project_name, "RIBS_", "")) %>% 
  mutate(project_name = str_replace(project_name, " - ", "_")) %>% 
  mutate(project_name = str_replace(project_name, "_-_", "_")) %>% 
  mutate(project_name = str_replace_all(project_name, " ", "_")) %>% 
  mutate(chemical_name = tolower(chemical_name))

qaqc.output.bound <- qaqc.output.bound %>%
  select(project_name, sys_sample_code, sample_delivery_group, chemical_name, fraction, validator_qualifiers, interpreted_qualifiers, qaqc_date) %>%
  filter(chemical_name != "selenium") %>% 
  mutate(validated_yn = "Y") %>% 
  rename(VALIDATOR_QUAL_EXPLN = interpreted_qualifiers)
# Ignore selenium flags (erroneously reported by ALS; already removed from RESULT file)

```

Join flags and related fields to results table
```{r}
result.all <- result.all %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  select(-validated_yn, -validator_qualifiers)

# Test various joins and compare to identify possible issues
result.all.flags.left <- left_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.all.flags.full <- full_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# Resulting left and full joins are identical (no recs left behind)

result.all.flags.inner <- inner_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# matches number of QAQC records in chunk above (all have match)

# Do antijoin to make sure non-joined records are all lab and QC samples.
result.all.flags.anti <- anti_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.sample.anti <- right_join(sample.all, result.all.flags.anti, by = c("sys_sample_code", "sample_delivery_group"))

# filter to non-lab and QC samples to verify what's missing was intentional (Ausable, Qaussaic, Duane Lake, PCBs)

result.sample.anti.sub <- result.sample.anti %>% 
  filter(sample_type_code %in% "N",
         DEC_sample_type %in% "N") 

# > sort(unique(result.sample.anti.sub$SITE_ID))
#  [1] "03-EMIL-5.1"       "10-CHUB-5.0"       "10-CHUB_T4-0.6"    "10-CHUB_T4-0.7"    "10-NMOW_T1-1.7"    "10-NMOW_T1-1.8"    "10-SABL_W-10.3"    "10-SABL_W-12.9"    "10-SABL_W-15.1"   
# [10] "10-SABL_W-18.6"    "10-SABL_W-20.7"    "10-SABL_W_T13-0.1" "10-SABL_W_T13-0.2" "10-SABL_W_T14-0.2" "10-SABL_W_T14-0.3" "10-SABL_W_T26-0.1" "10-SABL_W_T26-0.2" "10-SABL_W_T27-0.1"
# [19] "10-SABL_W_T27-0.2" "11-UHUD-2.7"       "12-LDUAN_T1-0.1"   "12-MOHK-1.5"       "12-MOHK-13.4"      "12-MOHK-17.3"      "12-MOHK-24.0"      "13-WQUAS-9.8"   

# All above sites are PCBs, Ausable, Duane Lake. Mohawk sites present are likely DBP surrogate parameters that we don't flag and don't need to retain. Double checking this below.

result.sample.anti.sub.mohk <- result.sample.anti.sub %>% 
  filter(grepl("MOHK|UHUD", SITE_ID))

# > unique(result.sample.anti.sub.mohk$chemical_name)
# [1] "p-bromofluorobenzene"                        "dibromofluoromethane"                        "toluene-d8"                                  "2,3-dibromopropionic acid"                  
# [5] "1-bromo-4-fluorobenzene bromofluorobenzene)"
# Confirmed, above are DBP surrograte params that we do not flag.

#  Look for duplicate records (possible issues with join)
dups <- result.all.flags.full %>% 
  group_by(sys_sample_code, sample_delivery_group, chemical_name, fraction) %>% 
  mutate(dups = n()) %>% 
  filter(dups > 1)
 # Only dups present are with PCBs and they are present in the raw EDDs.

# Clean up dataframes and rename
result.all <- result.all.flags.full
rm(qaqc.output.bound, result.all.flags.left, result.all.flags.full, result.all.flags.inner, result.all.flags.anti, result.sample.anti, result.sample.anti.sub, result.sample.anti.sub.mohk, dups)

```

Flag any field results not run through QAQC (Duane Lake, Quassiac Creek, Ausable 2018)
```{r}
# Join sample type field from SAMPLE table to gather required info for filtering
sample.all.type <- sample.all %>% 
  select(SITE_ID, sys_sample_code, sample_source, sample_delivery_group, DEC_sample_type, sample_type_code)
result.all.type <- left_join(result.all, sample.all.type, by = c("sys_sample_code", "sample_delivery_group")) %>% 
  # select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, validator_qualifiers, VALIDATOR_QUAL_EXPLN, everything())
  select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, everything())

# Check what types of samples got flags
result.all.type.check <- result.all.type %>% 
  select(validator_qualifiers, DEC_sample_type) %>% 
  distinct()

# Filter out normal samples that didn't get flags to verify that only the ones intentionally not flagged are there.
result.all.notflagged.n <- result.all.type %>% 
  filter(is.na(validator_qualifiers),
         DEC_sample_type %in% "N",
         sample_source %in% "Field")

# List output below as expected. EMIL, MOHK+UHUD-2.7 sites had parameters that we don't flag, and the remaining are sites from projects with QAQC errors or insufficient QAQC samples were collected.
# > sort(unique(result.all.notflagged.n$SITE_ID))
#  [1] "03-EMIL-5.1"       "10-CHUB-5.0"       "10-CHUB_T4-0.6"    "10-CHUB_T4-0.7"    "10-NMOW_T1-1.7"    "10-NMOW_T1-1.8"    "10-SABL_W-10.3"    "10-SABL_W-12.9"    "10-SABL_W-15.1"   
# [10] "10-SABL_W-18.6"    "10-SABL_W-20.7"    "10-SABL_W_T13-0.1" "10-SABL_W_T13-0.2" "10-SABL_W_T14-0.2" "10-SABL_W_T14-0.3" "10-SABL_W_T26-0.1" "10-SABL_W_T26-0.2" "10-SABL_W_T27-0.1"
# [19] "10-SABL_W_T27-0.2" "11-UHUD-2.7"       "12-LDUAN_T1-0.1"   "12-MOHK-1.5"       "12-MOHK-13.4"      "12-MOHK-17.3"      "12-MOHK-24.0"      "13-WQUAS-9.8"   


# Mark validated_yn as "N" for all those above then add NF flags and explanations to all those above except EMIL and MOHK+UHUD-2.7 sites.
 
result.all.flagged2 <- result.all.type %>% 
  mutate(validated_yn = ifelse(
    is.na(validator_qualifiers) &
      DEC_sample_type %in% "N" &
      sample_source %in% "Field",
    "N", validated_yn)) %>% 
  mutate(validator_qualifiers = ifelse(
    is.na(validator_qualifiers) &
      DEC_sample_type %in% "N" &
      sample_source %in% "Field" &
      !grepl("*EMIL", SITE_ID) &
      !grepl("*UHUD", SITE_ID) &    # Added 2020-10-05
      !grepl("*MOHK", SITE_ID), 
    "NF", validator_qualifiers)) %>% 
  mutate(VALIDATOR_QUAL_EXPLN = ifelse(validator_qualifiers %in% "NF", 
    "Not flagged due to QAQC error or insufficient QAQC sampling", VALIDATOR_QUAL_EXPLN)) 

# Veryify that only remaining field "N" samples without flags are those params we don't flag (PCBs and 5 DBP surrogate params)
result.all.flagged2.naflags <- result.all.flagged2 %>% 
  filter(is.na(validator_qualifiers),
         sample_source %in% "Field",
         DEC_sample_type %in% "N")
# Above checks out :)

# Clean up new result table and remove joined fields
result.all.flagged2 <- result.all.flagged2 %>% 
  # select(everything(), validator_qualifiers, VALIDATOR_QUAL_EXPLN, qaqc_date, validated_yn) %>% 
  select(-SITE_ID, -sample_source, -DEC_sample_type, -sample_type_code) 

rm(sample.all.type, result.all.type, result.all.type.check, result.all.notflagged.n, result.all.flagged2.naflags)


```

Fix EB samples misidentified as FB in ALS data
```{r}

# Find sys_sample_codes that have FB but are not mercury results
result.badFBs <- result.all.flagged2 %>% 
  filter(grepl("*FB", sys_sample_code),
         !grepl("mercury", chemical_name)
  )

badFB.SSCs <- result.badFBs %>% 
  select(sys_sample_code) %>% 
  distinct() %>% 
  # Adde EB field to list of bad SSCs to join 
  mutate(DEC_sample_type.corr = "EB")

# Pull list of matching samples in SAMPLE table and check if all FBs
sample.badFB.match <- sample.all %>% 
  filter(sys_sample_code %in% badFB.SSCs$sys_sample_code)

# Change DEC sample type codes for the list above from FB to EB
sample.all <- sample.all %>% 
  left_join(badFB.SSCs, by = "sys_sample_code") %>% 
  mutate(DEC_sample_type = ifelse(DEC_sample_type.corr %in% "EB", "EB", DEC_sample_type)) %>% 
  select(-DEC_sample_type.corr)

rm(result.badFBs, badFB.SSCs, sample.badFB.match)

```

Fix inconsistent lab_qualifiers and interpreted_qualifiers fields (subcontracted data uses commas)
```{r}
# Make table of unique flags and test methods of removing special characters
labflags <- result.all.flagged2 %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()
  
labflags.edit <- labflags %>%
  mutate(lab_qualifiers2 = str_replace_all(lab_qualifiers, "[^[:alnum:]]", "")) %>% 
  mutate(interpreted_qualifiers2 = str_replace_all(interpreted_qualifiers, "[^[:alnum:]]", ""))

result.all.flagged2 <- result.all.flagged2 %>% 
  mutate(lab_qualifiers = str_replace_all(lab_qualifiers, "[^[:alnum:]]", "")) %>% 
  mutate(interpreted_qualifiers = str_replace_all(interpreted_qualifiers, "[^[:alnum:]]", ""))
  
labflags.new <- result.all.flagged2 %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()

rm(labflags, labflags.edit, labflags.new)

```

Join pcodes field using "pcode join table" (based on chemical_name, fraction, and unit)
```{r}

# Import pcodes 
pcode_path <- file.path("C:/Users/gmlemley/New York State Office of Information Technology Services/SMAS - Streams Data Modernization/to_be_cleaned/chem_parameters")
pcode.join <- readxl::read_excel(file.path(pcode_path, "pcode_join_table_CLEAN_2020-06-25.xlsx")) %>% 
  select(RESULT_TYPE, everything()) %>% 
  select(-"Has duplicate", -"Notes") %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  mutate(result_unit = tolower(result_unit)) %>% 
  mutate(DEC_pcode_FINAL = formatC(DEC_pcode_FINAL, width = 3, format = "d", flag = "0")) %>% 
  # Remove instances of duplicate rows that represented differing unit capitalization (will just do this in the data) 
  distinct()

# Export cleaned pcode table for sending to LMAS
# write.csv(pcode.join, file.path(root.dir, "parameters", "dec_pcode_join_2020-08-24.csv"), row.names = FALSE)

# Filter to lab only for joining to chem data
pcode.join.lab <- pcode.join %>% 
  filter(RESULT_TYPE %in% "lab") %>%
  select(-RESULT_TYPE)

# Join to chem results table
result.all.pcodes <- left_join(result.all.flagged2, pcode.join.lab, by = c("chemical_name", "fraction", "result_unit")) %>% 
  select(DEC_pcode_FINAL, chemical_name, everything())

# Review records that didn't get pcodes assigned
result.all.pcodes.na <- result.all.pcodes %>% 
  filter(is.na(DEC_pcode_FINAL))
rm(result.all.pcodes.na)

# Populate missing pcodes (PCBs)
result.all.pcodes <- result.all.pcodes %>% 
  mutate(DEC_pcode_FINAL = ifelse(is.na(DEC_pcode_FINAL) & result_unit %in% "pg/l", 168, DEC_pcode_FINAL)) %>% 
  mutate(DEC_pcode_FINAL = ifelse(is.na(DEC_pcode_FINAL) & result_unit %in% "percent", 169, DEC_pcode_FINAL))

# summarize join for review  
# result.all.pcodes.check <- result.all.pcodes %>% 
#   select(DEC_pcode_FINAL, chemical_name, fraction, result_unit) %>% 
#   distinct()

result.all <- result.all.pcodes

rm(result.all.pcodes, pcode.join, pcode.join.lab, result.all.flagged2)


```

Fix bad dates from ALS
```{r}
# Correct bad years in sample_date and analysis_date fields (for just a handful lab QC samples of TDS and chlorophyll-a results)

## SAMPLE

# Find bad years
sample.all.datecheck <- sample.all %>% 
  filter(!grepl("*2018", sample_date)) %>% 
  filter(!grepl("*2019", sample_date))

# Test mutation
sample.all.datecheck <- sample.all.datecheck %>% 
  mutate(sample_date = str_replace(sample_date, "1999", "2019")) %>% 
  mutate(sample_date = str_replace(sample_date, "2016", "2019"))

# Perform mutation
sample.all.corr <- sample.all %>% 
  mutate(sample_date = str_replace(sample_date, "1999", "2019")) %>% 
  mutate(sample_date = str_replace(sample_date, "2016", "2019"))

sample.all <- sample.all.corr

rm(sample.all.datecheck, sample.all.corr)


## RESULT

# Find bad years
result.all.form.datecheck <- result.all %>% 
  filter(!grepl("*2018", analysis_date)) %>% 
  filter(!grepl("*2019", analysis_date))

# Test mutation
result.all.form.datecheck <- result.all.form.datecheck %>% 
  mutate(analysis_date = str_replace(analysis_date, "1999", "2019")) %>% 
  mutate(analysis_date = str_replace(analysis_date, "2016", "2019"))

# Perform mutation
result.all.corr <- result.all %>% 
  mutate(analysis_date = str_replace(analysis_date, "1999", "2019")) %>% 
  mutate(analysis_date = str_replace(analysis_date, "2016", "2019"))

result.all <- result.all.corr

rm(result.all.form.datecheck, result.all.corr)


## BATCH

# Find bad years
batch.all.form.datecheck <- batch.all %>% 
  filter(!grepl("*2018", analysis_date)) %>% 
  filter(!grepl("*2019", analysis_date))

# Test mutation
batch.all.form.datecheck <- batch.all.form.datecheck %>% 
  mutate(analysis_date = str_replace(analysis_date, "1999", "2019")) %>% 
  mutate(analysis_date = str_replace(analysis_date, "2016", "2019"))

# Perform mutation
batch.all.corr <- batch.all %>% 
  mutate(analysis_date = str_replace(analysis_date, "1999", "2019")) %>% 
  mutate(analysis_date = str_replace(analysis_date, "2016", "2019"))

batch.all <- batch.all.corr

rm(batch.all.form.datecheck, batch.all.corr)


```

Reformat field names and add blank fields
```{r}

## Join project name to sample table for exporting for Charlie (to verify project table)
# result.projnames <- result.all %>% 
#   select(sample_delivery_group, project_name) %>% 
#   filter(!is.na(project_name)) %>% 
#   unique()
# sample.all.projnames <- left_join(sample.all, result.projnames, by = "sample_delivery_group") %>%
#   select(project_name, sample_date, everything()) %>%
#   filter(sample_source %in% "Field")
# write.table(sample.all.projnames, file = file.path(root.dir, "data", "2018-2019_ITS_2020-08-25", "chem_sample_2018-2019_fieldonly_projnames.csv"),sep=",", row.names = FALSE)


sample.all.form <- sample.all %>%
  rename_all(toupper) %>%
  rename(
    EVENT_SMAS_HISTORY_ID = SITE_ID,
    DEC_SAMPLE_TYPE_CDE = DEC_SAMPLE_TYPE,
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    SAMPLE_MATRIX_CDE = SAMPLE_MATRIX_CODE,
    LAB_SAMPLE_TYPE_CDE = SAMPLE_TYPE_CODE,
    PARENT_SAMPLE_CDE = PARENT_SAMPLE_CODE,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP,
    SYS_LOC_CDE = SYS_LOC_CODE,
    SAMPLE_DATETIME = SAMPLE_DATE,
    SITE_ID_CORR = SITE_ID_CORR_IND
  ) %>%
  mutate(SAMPLE_DATETIME.posixct = as.POSIXct(SAMPLE_DATETIME, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(EVENT_SMAS_SAMPLE_DATE = strftime(SAMPLE_DATETIME.posixct, "%m/%d/%Y")) %>%
  rename_all(function(x)
    paste0("CHS_", x))
# mutate(EVENT_SMAS_ID = paste0(CHS_SITE_ID,"_",EVENT_ID_DATE))

result.all.form <- result.all %>%
  rename_all(toupper) %>%
  mutate(QLFR_SRC = "AE") %>% 
  rename(
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME,
    LAB_MATRIX_CDE = LAB_MATRIX_CODE,
    LAB_NAME_CDE = LAB_NAME_CODE,
    SUBSAMPLE_AMT = SUBSAMPLE_AMOUNT,
    SUBSAMPLE_AMT_UNIT = SUBSAMPLE_AMOUNT_UNIT,
    RESULT_TYPE_CDE = RESULT_TYPE_CODE,
    REPORTABLE_RESULT_IND = REPORTABLE_RESULT,
    LAB_QUAL = LAB_QUALIFIERS,
    VALIDATOR_QUAL = VALIDATOR_QUALIFIERS,
    INTERPRETED_QUAL = INTERPRETED_QUALIFIERS,
    VALIDATED_IND = VALIDATED_YN,
    METHOD_DETECT_LIMIT = METHOD_DETECTION_LIMIT,
    REPORTING_DETECT_LIMIT = REPORTING_DETECTION_LIMIT,
    QC_ORIG_CONC = QC_ORIGINAL_CONC,
    QC_DUP_ORIG_CONC = QC_DUP_ORIGINAL_CONC,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP,
    VALIDATION_DATE = QAQC_DATE
  ) %>%
  # mutate(
  #   VALIDATOR_QUAL_REASON_CDE = "",
  #   VALIDATOR_SAMPLE_ACCURACY = "",
  #   VALIDATOR_SAMPLE_PRECISION_FIELD = "",
  #   VALIDATOR_SAMPLE_PRECISION_LAB = "",
  #   VALIDATOR_SAMPLE_EQUIP_BLANK = "",
  #   VALIDATOR_SAMPLE_PARAM_PAIR = "",
  #   VALIDATOR_QUAL_EXPLN = "",
  #   VALIDATION_DATE = "",
  #   LAB_VALIDATION_LEVEL = NA
  # ) %>%
  # mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  # mutate(PREP_DATE = as.POSIXct(PREP_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(VALIDATION_DATE = as.Date(VALIDATION_DATE, format = "%m/%d/%Y"),
         VALIDATION_DATE = format((VALIDATION_DATE), "%m/%d/%Y")) %>% 
  mutate(FRACTION = case_when(
    FRACTION == "T" ~ "TOTAL",
    FRACTION == "D" ~ "DISSOLVED",
    TRUE ~ FRACTION)) %>% 
  rename_all(function(x)
    paste0("CHR_", x)) %>% 
  rename(CHR_PCODE = CHR_DEC_PCODE_FINAL)
    # fixed above from CHEM_PCODE on 9/11/20.

batch.all.form <- batch.all %>%
  rename_all(toupper) %>%
  rename(SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
         LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME) %>%
  # mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(FRACTION = case_when(
    FRACTION == "T" ~ "TOTAL",
    FRACTION == "D" ~ "DISSOLVED",
    TRUE ~ FRACTION)) %>% 
  rename_all(function(x)
    paste0("CHB_", x))

```

Select final headers as per ITS data model (copied from compile_2017-2019.Rmd)
```{r}
# Headers selections below copied directly from the data dictionary, 3/27/20.

# SAMPLE table
sample.all.FINAL <- sample.all.form %>% 
    select(CHS_EVENT_SMAS_HISTORY_ID, CHS_EVENT_SMAS_SAMPLE_DATE, CHS_SITE_ID_CORR, CHS_DATA_PROVIDER, CHS_SYS_SAMPLE_CDE, 
           CHS_SAMPLE_NAME, CHS_SAMPLE_MATRIX_CDE, CHS_DEC_SAMPLE_TYPE_CDE, CHS_LAB_SAMPLE_TYPE_CDE, CHS_SAMPLE_SOURCE, 
           CHS_PARENT_SAMPLE_CDE, CHS_SAMPLE_DEL_GRP, CHS_SAMPLE_DATETIME, CHS_SAMPLE_RECEIPT_DATE, CHS_SYS_LOC_CDE,
           CHS_CHAIN_OF_CUSTODY, CHS_SAMPLER, CHS_SAMPLING_COMPANY_CODE, CHS_COMMENT)

# RESULT table
result.all.FINAL <- result.all.form %>% 
  select(CHR_PCODE, CHR_SYS_SAMPLE_CDE, CHR_SAMPLE_DEL_GRP, CHR_LAB_ANAL_METHOD_NAME, CHR_ANALYSIS_DATE, CHR_FRACTION, CHR_TEST_TYPE, CHR_LAB_MATRIX_CDE, 
         CHR_DILUTION_FACTOR, CHR_PREP_METHOD, CHR_PREP_DATE, CHR_LAB_NAME_CDE, CHR_QC_LEVEL, CHR_LAB_SAMPLE_ID, CHR_SUBSAMPLE_AMT, 
         CHR_SUBSAMPLE_AMT_UNIT, CHR_FINAL_VOLUME, CHR_FINAL_VOLUME_UNIT, CHR_CAS_RN, CHR_CHEMICAL_NAME, CHR_RESULT_VALUE, CHR_RESULT_UNIT, 
         CHR_RESULT_TYPE_CDE, CHR_REPORTABLE_RESULT_IND, CHR_DETECT_FLAG, CHR_QLFR_SRC, CHR_LAB_QUAL, CHR_INTERPRETED_QUAL, CHR_VALIDATED_IND, CHR_VALIDATION_DATE, CHR_VALIDATOR_QUAL, 
         CHR_VALIDATOR_QUAL_EXPLN, CHR_METHOD_DETECT_LIMIT, 
         CHR_REPORTING_DETECT_LIMIT, CHR_QUANTITATION_LIMIT, CHR_DETECTION_LIMIT_UNIT, CHR_RESULT_COMMENT, CHR_QC_ORIG_CONC, 
         CHR_QC_SPIKE_ADDED, CHR_QC_SPIKE_MEASURED, CHR_QC_SPIKE_RECOVERY, CHR_QC_DUP_ORIG_CONC, CHR_QC_DUP_SPIKE_ADDED, CHR_QC_DUP_SPIKE_MEASURED, 
         CHR_QC_DUP_SPIKE_RECOVERY, CHR_QC_RPD, CHR_QC_SPIKE_LCL, CHR_QC_SPIKE_UCL, CHR_QC_RPD_CL, CHR_QC_SPIKE_STATUS, CHR_QC_DUP_SPIKE_STATUS, 
         CHR_QC_RPD_STATUS)

# BATCH table
batch.all.FINAL <- batch.all.form %>% 
    select(CHB_SYS_SAMPLE_CDE, CHB_LAB_ANAL_METHOD_NAME, CHB_ANALYSIS_DATE, 
           CHB_FRACTION, CHB_TEST_TYPE, CHB_TEST_BATCH_TYPE, CHB_TEST_BATCH_ID)

```

Modify data further as needed to meet ITS submission guidelines
```{r}
# library(datetime)
# 
# sample.all.form <- sample.all.form %>%
#   mutate(CHS_SAMPLE_DATE = as.POSIXct(CHS_SAMPLE_DATE, format = "%m/%d/%Y %H:%M:%S"),
#          CHS_SAMPLE_DATE_2 = format((CHS_SAMPLE_DATE), "%m/%d/%Y %H:%M:%S"),
#          CHS_SAMPLE_RECEIPT_DATE = as.Date(CHS_SAMPLE_RECEIPT_DATE, format = "%m/%d/%Y"),
#          CHS_SAMPLE_RECEIPT_DATE_2 = format((CHS_SAMPLE_RECEIPT_DATE), "%m/%d/%Y"))

# Not needed since data comes in the format that ITS (Cindy) is requesting. BUT Retain above code for future reference when similar formatting is needed. This was tricky...

```


Test table joins
```{r}
test.sample.result <- left_join(result.all, sample.all, by = c("sys_sample_code", "sample_delivery_group")) 
# checks out okay
rm(test.sample.result)

test.result.pcode <- result.all %>% 
  rename(CHEM_PARAMETER_PCODE = DEC_pcode_FINAL) %>% 
  left_join(pcode.final, by = "CHEM_PARAMETER_PCODE") %>% 
  select(CHEM_PARAMETER_PCODE, CHEM_PARAMETER_NAME, chemical_name, CHEM_PARAMETER_UNIT, result_unit, CHEM_PARAMETER_FRACTION, fraction) %>% 
  unique()
rm(test.result.pcode)

# Import Keleigh's qualifier tables




```



Export 2018-2019 chem tables 
```{r}

write.table(sample.all.FINAL, file = file.path(root.dir, "data", "2018-2019_ITS_2020-10-05", "S_CHEM_HISTORY_SAMPLE_2020-10-07.csv"),sep=",", row.names = FALSE, na = "")
write.table(result.all.FINAL, file = file.path(root.dir, "data", "2018-2019_ITS_2020-10-05", "S_CHEM_HISTORY_RESULT.csv"),sep=",", row.names = FALSE, na = "")
write.table(batch.all.FINAL, file = file.path(root.dir, "data", "2018-2019_ITS_2020-10-05", "S_CHEM_HISTORY_BATCH.csv"),sep=",", row.names = FALSE, na = "")

```


Look at unique flags in 2001-2019 data (for Keleigh, creating lab_qualifiers reference table)
```{r}
# Import equis, 2016, and 2017 from other Rmds in this project first.

equis.result.flags <- equis.result %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()
result.2016.flags <- result.2016 %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()
result.2017.flags <- RESULT.2017 %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()
result.2019.2019.flags <- result.all %>% 
  select(lab_qualifiers, interpreted_qualifiers) %>% 
  distinct()

# See when lab_qual and interp_qual differ
result.all.flagdiff <- result.all %>% 
  mutate(flagdiff = ifelse(lab_qualifiers != interpreted_qualifiers, 1, 0)) %>% 
  select(flagdiff, lab_qualifiers, interpreted_qualifiers, everything())

result.equis.flagdiff <- equis.result %>% 
  mutate(flagdiff = ifelse(lab_qualifiers != interpreted_qualifiers, 1, 0)) %>% 
  select(flagdiff, lab_qualifiers, interpreted_qualifiers, everything())

result.2017.flagdiff <- RESULT.2017 %>% 
  mutate(flagdiff = ifelse(lab_qualifiers != interpreted_qualifiers, 1, 0)) %>% 
  select(flagdiff, lab_qualifiers, interpreted_qualifiers, everything())

result.2016.flagdiff <- result.2016 %>% 
  mutate(flagdiff = ifelse(lab_qualifiers != interpreted_qualifiers, 1, 0)) %>% 
  select(flagdiff, lab_qualifiers, interpreted_qualifiers, everything())

  
flags.all <- bind_rows(equis.result.flags, result.2016.flags, result.2017.flags, result.2019.2019.flags) %>% 
  select(interpreted_qualifiers) %>% 
  distinct()

write.table(flags.all, file = file.path(root.dir, "flags", "2001-2019_unique_qualifiers_2020-08-27.csv"),sep=",")
```


