---
title: "compile_2020"
output: html_document
---


```{r Load in libs, set project dirs}
library(tidyverse)

root.dir <- rprojroot::find_root("chem_hist_cleaning.Rproj")
target.dir <- file.path(root.dir, "data", "2021", "assmnts")
qaqc_dir <- file.path(target.dir, "qaqc_output")
datamod.dir <- "C:/Users/gmlemley/New York State Office of Information Technology Services/SMAS - Streams Data Modernization/Cleaned Files/"

```

Import sample and result files exported from Chem_raw_processing.Rproj
```{r Import data}
sample.all <- read.csv(file.path(target.dir, "2021_chem_preqaqc_SAMPLE-all_subset_assmnts_v2_2021-10-27.csv"), stringsAsFactors = FALSE)
result.all <- read.csv(file.path(target.dir, "2021_chem_preqaqc_RESULT-all_subset_assmnts_v2_2021-10-27.csv"), stringsAsFactors = FALSE,
                       colClasses = c(fraction="character")
) %>% 
  rename(sample_delivery_group = lab_sdg)

```

Test join by sys_sample_code and SDG
```{r Initial join test}
test_join_sample.result <- full_join(sample.all, result.all, by = c("sys_sample_code", "sample_delivery_group"))

# CHECKS OUT OKAY. Same number of records created in joined table as in RESULT table.

rm(test_join_sample.result)
```

Import and bind flags from QAQC output files
```{r Import QAQC flags}
# Import all qaqc output files in subdir and bind together as a dataframe
setwd(qaqc_dir)
qaqc.output.bound <- list.files(path = qaqc_dir, pattern = "*.csv") %>% 
  map_df(~read_csv(.,  col_types = cols(fraction = col_character()))) %>% 
  # mutate(project_name = str_replace(project_name, "RIBS_", "")) %>% 
  # mutate(project_name = str_replace(project_name, " - ", "_")) %>% 
  # mutate(project_name = str_replace(project_name, "_-_", "_")) %>% 
  # mutate(project_name = str_replace_all(project_name, " ", "_")) %>% 
  mutate(chemical_name = tolower(chemical_name))

# Select only fields needed to join to results table and mark all as validated 
qaqc.output.bound <- qaqc.output.bound %>%
  select(project_name, sys_sample_code, sample_delivery_group, chemical_name, fraction, validator_qualifiers, interpreted_qualifiers, qaqc_date) %>%
  mutate(validated_yn = "Y") %>%
  rename(VALIDATOR_QUAL_EXPLN = interpreted_qualifiers)

```

Join flags and related fields to results table
```{r Join QAQC flags}
result.all <- result.all %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  select(-validated_yn, -validator_qualifiers)

# Test various joins and compare to identify possible issues
result.all.flags.left <- left_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.all.flags.full <- full_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# Resulting left and full joins are identical (no recs left behind)

result.all.flags.inner <- inner_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
# matches number of QAQC records in chunk above (all have match)

# Do antijoin to make sure non-joined records are all lab and QC samples.
result.all.flags.anti <- anti_join(result.all, qaqc.output.bound, by = c("sys_sample_code", "sample_delivery_group", "chemical_name", "fraction"))
result.sample.anti <- right_join(sample.all, result.all.flags.anti, by = c("sys_sample_code", "sample_delivery_group"))

# filter to non-lab and QC samples to verify what's missing was intentional (or that data frame is blank, as it should be)

result.sample.anti.sub <- result.sample.anti %>% 
  filter(sample_type_code %in% "N",
         DEC_sample_type %in% "N") 

# Found: none

#  Look for duplicate records (possible issues with join)
dups <- result.all.flags.full %>% 
  group_by(sys_sample_code, sample_delivery_group, chemical_name, fraction) %>% 
  mutate(dups = n()) %>% 
  filter(dups > 1)
 # Found: None.

# Clean up dataframes and rename
result.all <- result.all.flags.full
rm(qaqc.output.bound, result.all.flags.left, result.all.flags.full, result.all.flags.inner, result.all.flags.anti, result.sample.anti, result.sample.anti.sub, dups)

```

Flag any field results not run through QAQC
```{r Populated flags fir non-QAQCd data}
# Join sample type field from SAMPLE table to gather required info for filtering
sample.all.type <- sample.all %>% 
  select(SITE_ID, sys_sample_code, sample_source, sample_delivery_group, DEC_sample_type, sample_type_code)
result.all.type <- left_join(result.all, sample.all.type, by = c("sys_sample_code", "sample_delivery_group")) %>% 
  # select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, validator_qualifiers, VALIDATOR_QUAL_EXPLN, everything())
  select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, everything())

# Check what types of samples got flags
result.all.type.check <- result.all.type %>% 
  select(validator_qualifiers, DEC_sample_type) %>% 
  distinct()

# Filter out normal samples that didn't get flags to verify that only the ones intentionally not flagged are there.
result.all.notflagged.n <- result.all.type %>% 
  filter(is.na(validator_qualifiers),
         DEC_sample_type %in% "N",
         sample_source %in% "Field")

# Found: None present.

# Mark validated_yn as "N" for all those above then add NF flags and explanations to all those above 

result.all.flagged2 <- result.all.type %>% 
  mutate(validated_yn = ifelse(
    is.na(validator_qualifiers) &
      DEC_sample_type %in% "N" &
      sample_source %in% "Field",
    "N", validated_yn)) 
  # mutate(validator_qualifiers = ifelse(
  #   is.na(validator_qualifiers) &
  #     DEC_sample_type %in% "N" &
  #     sample_source %in% "Field" &
  #     !grepl("*EMIL", SITE_ID) &
  #     !grepl("*UHUD", SITE_ID) &    # Added 2020-10-05
  #     !grepl("*MOHK", SITE_ID), 
  #   "E", validator_qualifiers)) %>% 
  # mutate(VALIDATOR_QUAL_EXPLN = ifelse(validator_qualifiers %in% "E", 
  #   "Not flagged due to QAQC error or insufficient QAQC sampling", VALIDATOR_QUAL_EXPLN)) 

# Verify that only remaining field "N" samples without flags are those params we don't flag (PCBs and 5 DBP surrogate params)
result.all.flagged2.naflags <- result.all.flagged2 %>% 
  filter(is.na(validator_qualifiers),
         sample_source %in% "Field",
         DEC_sample_type %in% "N")
# Above checks out :)

# Clean up new result table and remove joined fields
result.all.flagged2 <- result.all.flagged2 %>% 
  select(-SITE_ID, -sample_source, -DEC_sample_type, -sample_type_code) 

rm(sample.all.type, result.all.type, result.all.type.check, result.all.notflagged.n, result.all.flagged2.naflags)


```


Join pcodes field using "pcode join table" (based on chemical_name, fraction, and unit)
```{r Join pcodes}

# Import pcodes 
# pcode_path <- file.path("C:/Users/gmlemley/New York State Office of Information Technology Services/SMAS - Streams Data Modernization/to_be_cleaned/chem_parameters")
# pcode.join <- readxl::read_excel(file.path(pcode_path, "pcode_join_table_CLEAN_2020-06-25.xlsx")) %>% 
pcode.join <- read_csv(file.path(root.dir, "parameters", "dec_pcode_join_2021-04-14.csv")) %>%
  select(RESULT_TYPE, everything()) %>% 
  # select(-"Has duplicate", -"Notes") %>% 
  mutate(chemical_name = tolower(chemical_name)) %>% 
  mutate(result_unit = tolower(result_unit)) %>% 
  # mutate(DEC_pcode_FINAL = formatC(DEC_pcode_FINAL, width = 3, format = "d", flag = "0")) %>% 
  # Remove instances of duplicate rows that represented differing unit capitalization (will just do this in the data) 
  distinct()

# Export cleaned pcode table for sending to LMAS
# write.csv(pcode.join, file.path(root.dir, "parameters", "dec_pcode_join_2020-08-24.csv"), row.names = FALSE)

# Filter to lab only for joining to chem data
pcode.join.lab <- pcode.join %>% 
  filter(RESULT_TYPE %in% "lab") %>%
  select(-RESULT_TYPE)

# Join to chem results table
result.all.pcodes <- left_join(result.all.flagged2, pcode.join.lab, by = c("chemical_name", "fraction", "result_unit")) %>% 
  select(DEC_pcode_FINAL, chemical_name, everything())

# Return records that didn't get pcodes assigned
result.all.pcodes.na <- result.all.pcodes %>% 
  filter(is.na(DEC_pcode_FINAL))
sort(unique(result.all.pcodes.na$chemical_name))

# summarize join for review  
result.all.pcodes.check <- result.all.pcodes %>%
  select(DEC_pcode_FINAL, chemical_name, fraction, result_unit) %>%
  distinct()

result.all <- result.all.pcodes

rm(result.all.pcodes, pcode.join, pcode.join.lab, result.all.flagged2, result.all.pcodes.na, result.all.pcodes.check)


```


Reformat field names
```{r Reformat field names}

sample.all.form <- sample.all %>%
  rename_all(toupper) %>%
  rename(
    EVENT_SMAS_HISTORY_ID = SITE_ID,
    DEC_SAMPLE_TYPE_CDE = DEC_SAMPLE_TYPE,
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    SAMPLE_MATRIX_CDE = SAMPLE_MATRIX_CODE,
    LAB_SAMPLE_TYPE_CDE = SAMPLE_TYPE_CODE,
    PARENT_SAMPLE_CDE = PARENT_SAMPLE_CODE,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP,
    SYS_LOC_CDE = SYS_LOC_CODE,
    SAMPLE_DATETIME = SAMPLE_DATE,
    SITE_ID_CORR_YN = SITE_ID_CORR_IND
  ) %>%
  mutate(SAMPLE_DATETIME.posixct = as.POSIXct(SAMPLE_DATETIME, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(EVENT_SMAS_SAMPLE_DATE = strftime(SAMPLE_DATETIME.posixct, "%m/%d/%Y")) %>%
  rename_all(function(x)
    paste0("CHS_", x))
# mutate(EVENT_SMAS_ID = paste0(CHS_SITE_ID,"_",EVENT_ID_DATE))

result.all.form <- result.all %>%
  rename_all(toupper) %>%
  mutate(QLFR_SRC = "AE") %>% 
  rename(
    SYS_SAMPLE_CDE = SYS_SAMPLE_CODE,
    LAB_ANAL_METHOD_NAME = LAB_ANL_METHOD_NAME,
    LAB_MATRIX_CDE = LAB_MATRIX_CODE,
    LAB_NAME_CDE = LAB_NAME_CODE,
    SUBSAMPLE_AMT = SUBSAMPLE_AMOUNT,
    SUBSAMPLE_AMT_UNIT = SUBSAMPLE_AMOUNT_UNIT,
    RESULT_TYPE_CDE = RESULT_TYPE_CODE,
    # REPORTABLE_RESULT_IND = REPORTABLE_RESULT,
    LAB_QUAL = LAB_QUALIFIERS,
    VALIDATOR_QUAL = VALIDATOR_QUALIFIERS,
    INTERPRETED_QUAL = INTERPRETED_QUALIFIERS,
    # VALIDATED_IND = VALIDATED_YN,
    METHOD_DETECT_LIMIT = METHOD_DETECTION_LIMIT,
    REPORTING_DETECT_LIMIT = REPORTING_DETECTION_LIMIT,
    QC_ORIG_CONC = QC_ORIGINAL_CONC,
    QC_DUP_ORIG_CONC = QC_DUP_ORIGINAL_CONC,
    SAMPLE_DEL_GRP = SAMPLE_DELIVERY_GROUP,
    VALIDATION_DATE = QAQC_DATE
  ) %>%
  # mutate(ANALYSIS_DATE = as.POSIXct(ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  # mutate(PREP_DATE = as.POSIXct(PREP_DATE, format = "%m/%d/%Y %H:%M:%S")) %>%
  mutate(VALIDATION_DATE = as.Date(VALIDATION_DATE, format = "%m/%d/%Y"),
         VALIDATION_DATE = format((VALIDATION_DATE), "%m/%d/%Y")) %>% 
  mutate(FRACTION = case_when(
    FRACTION == "T" ~ "TOTAL",
    FRACTION == "D" ~ "DISSOLVED",
    TRUE ~ FRACTION)) %>% 
  rename_all(function(x)
    paste0("CHR_", x)) %>% 
  rename(CHR_PCODE = CHR_DEC_PCODE_FINAL)
    # fixed above from CHEM_PCODE on 9/11/20.

```

Select final headers as per ITS data model
```{r Select final columns}

# SAMPLE table
sample.all.FINAL <- sample.all.form %>% 
    select(CHS_EVENT_SMAS_HISTORY_ID, CHS_EVENT_SMAS_SAMPLE_DATE, CHS_SITE_ID_CORR_YN, CHS_DATA_PROVIDER, CHS_SYS_SAMPLE_CDE, 
           CHS_SAMPLE_NAME, CHS_SAMPLE_MATRIX_CDE, CHS_DEC_SAMPLE_TYPE_CDE, CHS_LAB_SAMPLE_TYPE_CDE, CHS_SAMPLE_SOURCE, 
           CHS_PARENT_SAMPLE_CDE, CHS_SAMPLE_DEL_GRP, CHS_SAMPLE_DATETIME, CHS_SAMPLE_RECEIPT_DATE, CHS_SYS_LOC_CDE,
           CHS_CHAIN_OF_CUSTODY, CHS_SAMPLER, CHS_SAMPLING_COMPANY_CODE, CHS_COMMENT)

# RESULT table
result.all.FINAL <- result.all.form %>% 
  select(CHR_PCODE, CHR_SYS_SAMPLE_CDE, CHR_SAMPLE_DEL_GRP, CHR_LAB_ANAL_METHOD_NAME, CHR_ANALYSIS_DATE, CHR_TEST_TYPE, CHR_LAB_MATRIX_CDE, 
         CHR_DILUTION_FACTOR, CHR_PREP_METHOD, CHR_PREP_DATE, CHR_LAB_NAME_CDE, CHR_QC_LEVEL, CHR_LAB_SAMPLE_ID, CHR_SUBSAMPLE_AMT, 
         CHR_SUBSAMPLE_AMT_UNIT, CHR_FINAL_VOLUME, CHR_FINAL_VOLUME_UNIT, CHR_CAS_RN, CHR_RESULT_VALUE, 
         CHR_RESULT_TYPE_CDE, CHR_REPORTABLE_RESULT, CHR_DETECT_FLAG, CHR_QLFR_SRC, CHR_LAB_QUAL, CHR_VALIDATED_YN, CHR_VALIDATION_DATE, CHR_VALIDATOR_QUAL, 
         CHR_VALIDATOR_QUAL_EXPLN, CHR_METHOD_DETECT_LIMIT, 
         CHR_REPORTING_DETECT_LIMIT, CHR_QUANTITATION_LIMIT, CHR_DETECTION_LIMIT_UNIT, CHR_RESULT_COMMENT, CHR_QC_ORIG_CONC, 
         CHR_QC_SPIKE_ADDED, CHR_QC_SPIKE_MEASURED, CHR_QC_SPIKE_RECOVERY, CHR_QC_DUP_ORIG_CONC, CHR_QC_DUP_SPIKE_ADDED, CHR_QC_DUP_SPIKE_MEASURED, 
         CHR_QC_DUP_SPIKE_RECOVERY, CHR_QC_RPD, CHR_QC_SPIKE_LCL, CHR_QC_SPIKE_UCL, CHR_QC_RPD_CL, CHR_QC_SPIKE_STATUS, CHR_QC_DUP_SPIKE_STATUS, 
         CHR_QC_RPD_STATUS)

```

Convert NAs to text for not_null fields (for coded tables)
```{r Convert NAs for non_nulls}
result.all.FINAL <- result.all.FINAL %>% 
  mutate(CHR_LAB_QUAL = ifelse(is.na(CHR_LAB_QUAL), 0, CHR_LAB_QUAL),
         CHR_LAB_QUAL = ifelse(CHR_LAB_QUAL %in% "", 0, CHR_LAB_QUAL),
         CHR_VALIDATOR_QUAL = ifelse(is.na(CHR_VALIDATOR_QUAL), 0, CHR_VALIDATOR_QUAL))
```

Generate list of unique values for review
```{r View unique values, eval = FALSE}

sample.unique <- lapply(sample.all.FINAL, unique)
result.unique <- lapply(result.all.FINAL, unique)

```

```{r Other final modifications}

# Change DEC sample type DUPs to SEQs (switched starting in 2020 to differentiate from old dup type)
# Format dates as dates to verify by sorting, then to the proper ITS format.
sample.all.FINAL <- sample.all.FINAL %>% 
  mutate(CHS_DEC_SAMPLE_TYPE_CDE = ifelse(CHS_DEC_SAMPLE_TYPE_CDE %in% "DUP", "SEQ", CHS_DEC_SAMPLE_TYPE_CDE),
         # Consider incorporating this into validation script (make SEQ to begin with and change to DUP in QAQC script's getting.started.R)
         CHS_DEC_SAMPLE_TYPE_CDE = ifelse(CHS_DEC_SAMPLE_TYPE_CDE %in% "N_DUPPARENT", "N_SEQPARENT", CHS_DEC_SAMPLE_TYPE_CDE),
         # Below is already done in validation script
         # CHS_EVENT_SMAS_HISTORY_ID = ifelse(CHS_EVENT_SMAS_HISTORY_ID %in% "LAB_INTERNAL", "00-QAQC-0.0", CHS_EVENT_SMAS_HISTORY_ID),
         CHS_EVENT_SMAS_SAMPLE_DATE = as.Date(CHS_EVENT_SMAS_SAMPLE_DATE, format = "%m/%d/%Y"),
         CHS_EVENT_SMAS_SAMPLE_DATE = format((CHS_EVENT_SMAS_SAMPLE_DATE), "%m/%d/%Y"),
         CHS_SAMPLE_RECEIPT_DATE = as.Date(CHS_SAMPLE_RECEIPT_DATE, format = "%m/%d/%Y"),
         CHS_SAMPLE_RECEIPT_DATE = format((CHS_SAMPLE_RECEIPT_DATE), "%m/%d/%Y"),
         CHS_SAMPLE_DATETIME = as.POSIXct(CHS_SAMPLE_DATETIME, format = "%m/%d/%Y %H:%M:%S"),
         CHS_SAMPLE_DATETIME = format((CHS_SAMPLE_DATETIME), "%m/%d/%Y %H:%M:%S")
         )  

result.all.FINAL <- result.all.FINAL %>% 
  mutate(CHR_ANALYSIS_DATE = as.POSIXct(CHR_ANALYSIS_DATE, format = "%m/%d/%Y %H:%M:%S"),
         CHR_ANALYSIS_DATE = format((CHR_ANALYSIS_DATE), "%m/%d/%Y %H:%M:%S")
)

# 
# # Correct erroneous ALS sample date entries
# sample.all.FINAL <- sample.all.FINAL %>% 
#   mutate(CHS_EVENT_SMAS_SAMPLE_DATE = ifelse(CHS_SAMPLE_NAME %in% "01-CHAU-0.4-09162020-W-SEQ", "09/16/2020", CHS_EVENT_SMAS_SAMPLE_DATE),
#          CHS_SAMPLE_DATETIME = ifelse(CHS_SAMPLE_NAME %in% "01-CHAU-0.4-09162020-W-SEQ", "09/16/2020 10:30:00", CHS_SAMPLE_DATETIME),
#          CHS_EVENT_SMAS_SAMPLE_DATE = ifelse(CHS_SAMPLE_NAME %in% "12-MOHK-79.5-06152020-W", "06/15/2020", CHS_EVENT_SMAS_SAMPLE_DATE),
#          CHS_SAMPLE_DATETIME = ifelse(CHS_SAMPLE_NAME %in% "12-MOHK-79.5-06152020-W", "06/15/2020 12:00:00", CHS_SAMPLE_DATETIME),
#          CHS_EVENT_SMAS_SAMPLE_DATE = ifelse(CHS_SAMPLE_NAME %in% "08-BLCK-84.5-06152020-W", "06/15/2020", CHS_EVENT_SMAS_SAMPLE_DATE),
#          CHS_SAMPLE_DATETIME = ifelse(CHS_SAMPLE_NAME %in% "08-BLCK-84.5-06152020-W", "06/15/2020 09:00:00", CHS_SAMPLE_DATETIME)
#          )


```


```{r Crosscheck event IDs against Charlie's in-situ}

insitu.master <- readxl::read_excel(file.path(datamod.dir, "Final_SBU_Field_ITS", "Master_S_IN_SITU_WATER_CHEM_v3_created20211029.xlsx")) 

samp.eventid.check <- sample.all.FINAL %>% 
  mutate(event_id_date = as.Date(CHS_EVENT_SMAS_SAMPLE_DATE, format = "%m/%d/%Y"),
         event_id_date = format(event_id_date, "%Y%m%d"),
         EVENT_SMAS_ID = paste0(CHS_EVENT_SMAS_HISTORY_ID,"_",event_id_date)) %>% 
  filter(!CHS_EVENT_SMAS_HISTORY_ID %in% "00-QAQC-0.0",
         CHS_SAMPLE_SOURCE %in% "Field",
         !EVENT_SMAS_ID %in% insitu.master$EVENT_SMAS_ID)

#### FOUND 9 RECORDS WITHOUT MATCHES. RECTIFY DURING 2021 FULL DATA PROCESSING ######

```


```{r Test table joins}

test.sample.all.FINAL <- sample.all.FINAL %>% 
  rename(SSC = CHS_SYS_SAMPLE_CDE,
         SDG = CHS_SAMPLE_DEL_GRP)
test.result.all.FINAL <- result.all.FINAL %>% 
  rename(SSC = CHR_SYS_SAMPLE_CDE,
         SDG = CHR_SAMPLE_DEL_GRP)

test.sample.result <- left_join(test.sample.all.FINAL, test.result.all.FINAL, by = c("SSC", "SDG")) 
# checks out okay
rm(test.sample.all.FINAL, test.result.all.FINAL, test.sample.result)

```

```{r Test pcode join}

pcode <- read.csv(file.path(datamod.dir, "Final_Chemistry_ITS", "MASTER_S_CHEM_PARAMETER_2021-05-03.csv"), stringsAsFactors = FALSE, colClasses = "character") %>% 
  mutate(CHEM_PARAMETER_PCODE = as.integer(CHEM_PARAMETER_PCODE))
         # CHEM_PARAMETER_PCODE = sprintf("%03d", CHEM_PARAMETER_PCODE)) 


test.result.pcode <- result.all.form %>% 
  rename(CHEM_PARAMETER_PCODE = CHR_PCODE) %>% 
  left_join(pcode, by = "CHEM_PARAMETER_PCODE") %>% 
  select(CHEM_PARAMETER_PCODE, CHEM_PARAMETER_NAME, CHR_CHEMICAL_NAME, CHEM_PARAMETER_UNIT_NOSP, CHR_RESULT_UNIT,
         CHEM_PARAMETER_FRACTION, CHR_FRACTION) %>% 
  unique() %>% 
  mutate(CHR_CHEMICAL_NAME_caps = toupper(CHR_CHEMICAL_NAME))

```

Generate EVENT ID records for Charlie to crosscheck against, and append to survey event IDs
```{r Generate event IDs}
event.id <- sample.all.FINAL %>% 
  distinct(CHS_EVENT_SMAS_HISTORY_ID, CHS_EVENT_SMAS_SAMPLE_DATE)

```

Export tables
```{r Export tables, eval = FALSE}

# write.table(event.id, file = file.path(datamod.dir, "20210415_SMAS_chem_2020_event_IDs.csv"),sep=",", row.names = FALSE, na = "")
write.table(sample.all.FINAL, file = file.path(target.dir, "SMAS_chem_2021_stayCALM-SAMPLE_2021-10-29.csv"),sep=",", row.names = FALSE, na = "")
write.table(result.all.FINAL, file = file.path(target.dir, "SMAS_chem_2021_stayCALM-RESULT_2021-10-29.csv"),sep=",", row.names = FALSE, na = "")

```


